---
title: "Enriched Biodomain Terms & Pathtrace Input"
author: "Greg Cary"
date: "`r Sys.Date()`"
output: 
  html_document: 
    fig_width: 5
    fig_height: 4
  html_notebook:
    code_folding: hide
    theme: readable
    css: style.css
    toc: true
    toc_float: true
---
# Setup

```{r setup}
# # Package names
# packages <- c(
#   # 'paxtoolsr','org.Hs.eg.db','HotNetvieweR','clusterProfiler', 
#   'synapser','igraph','tidygraph','ggraph','tidyverse'
#   )
# 
# # Load packages
# invisible(lapply(packages, library, character.only = TRUE))

library(synapser)
library(googlesheets4)
library(igraph)
library(tidygraph)
library(ggraph)
library(tidyverse)

source('../../treatAD_biodomains/scripts/biodom_tally.R')
source('../../treatAD_biodomains/scripts/annotate_enr_term_biodomains.R')
source('../../treatAD_biodomains/scripts/biodom_enr_plots.R')

theme_set(theme_bw())
```

# Data
Grab relevant data from synapse, including:
1) Target Risk Scores ([syn25575156](https://www.synapse.org/#!Synapse:syn25575156){target="_blank"}) and Omics Scores ([syn22758536](https://www.synapse.org/#!Synapse:syn22758536){target="_blank"})   
2) Biodomain Definitions ([syn25428992](https://www.synapse.org/#!Synapse:syn25428992){target="_blank"})   
3) Biodomain Term Annotation Kappa scores ([syn51163744](https://www.synapse.org/#!Synapse:syn51163744){target="_blank"}) & Network ([syn51497240](https://www.synapse.org/#!Synapse:syn51497240){target="_blank"})   
3) Risk-enriched Biodomain Terms ([syn45824995](https://www.synapse.org/#!Synapse:syn45824995){target="_blank"})  
4) Risk-enriched Biodomain Term Network ([syn51387897](https://www.synapse.org/#!Synapse:syn51387897){target="_blank"})  
5) Base Network ([syn51110930](https://www.synapse.org/#!Synapse:syn51110930){target="_blank"})  

```{r}
synLogin()

# target risk scores
scores <- read_csv(
  synTableQuery('select * from syn25575156', includeRowIdAndRowVersion = F)$filepath
  , col_types = cols())

omics <- read_csv(
  synTableQuery('select * from syn22758536', includeRowIdAndRowVersion = F)$filepath
  , col_types = cols())

# biological domain annotations
biodom <- full_join(
  
  # biodomains
  readRDS(synGet('syn25428992')$path),
  
  # domain labels
  read_csv(synGet('syn26856828')$path, col_types = cols()),  
  
  by = c('Biodomain'='domain')
  ) %>% mutate(Biodomain = if_else(Biodomain == 'none', NA_character_, Biodomain))

domains = biodom %>% pull(Biodomain) %>% unique() %>% sort()

subdomains <- biodom %>% select(Biodomain, subdomain_idx, Subdomain) %>% 
  distinct() %>% filter(subdomain_idx != 0)

# # biodomain term annotation kappa scores
# biodom.kappa <- read_csv(synapser::synGet('syn51163744')$path) %>% 
#   left_join(., biodom %>% select(goid_1 = GO_ID, n_gene1 = n_symbol), by = 'goid_1') %>%
#   left_join(., biodom %>% select(goid_2 = GO_ID, n_gene2 = n_symbol), by = 'goid_2') %>%
#   distinct() %>%
#   filter(goid_1 != goid_2,
#          kappa > 0.1,
#          n_gene1 > 3,
#          n_gene2 > 3)

# biodomain term annotation network
biodom.nw <- igraph::read_graph(synGet('syn51497240')$path, format = 'graphml') 

# enriched biodomain terms
# enr.bd <- read_csv( synGet('syn45824995')$path, col_types = cols() ) %>% 
#   mutate(leadingEdge_genes = str_split(leadingEdge_genes, '\\|'))

enr.scores <- readRDS(
  '/projects/carter-lab/caryg/treatAD_biodomains/results/risk_score_biodom_enrichments.rds'
  )
enr.bd <- enr.scores$anno[[3]] %>% 
  mutate(leadingEdge_genes = str_split(core_enrichment, '\\/'))


# enriched biodomain term network
# enr.nw <- igraph::read_graph(synGet('syn51387897')$path, format = 'graphml') 

# base network
base.net <- igraph::read_graph(synGet('syn51110930')$path, format = 'graphml') 

# specify directed edge types
directed_edge_types = c("catalysis-precedes",
                        "controls-expression-of",
                        "controls-phosphorylation-of",
                        "controls-state-change-of",
                        "controls-transport-of"
                        )

```

## J Wiley draft sub-domains

So far just Synapse, Mitochondrial Metabolism, Immune Response, Epigenetics, and Lipid Metabolism  
```{r}
subdom <- readxl::read_xlsx(
  paste0(here::here(), '/data/Subendophenotype Trackers.xlsx'),
  sheet = 1, 
  col_names = T
)

subdom$Biodomain[which(subdom$Biodomain == 'Epigenetics')] <- 'Epigenetic'
```


## plot subnetwork
```{r}
plot_kd_subnet <- function(nw, kd, term) {
  
  vert_num <- match(kd, V(nw)$name)
  
  vert_neigh <- neighbors(nw, vert_num)
  
  term_num <- biodom %>%
    filter(GOterm_Name == term) %>%
    pull(symbol) %>% unlist() %>%
    match(., V(nw)$name) %>% .[!is.na(.)]
  
  g2 <- induced_subgraph(nw, c(vert_num, intersect(term_num, vert_neigh)))
  g3 <- induced_subgraph(nw, c(vert_num, term_num))
  
  cowplot::plot_grid(
    
    ggraph(g3, layout = 'linear', circular = TRUE) +
      geom_edge_arc(alpha = .3, color = 'grey75') +
      geom_node_point( shape = 21, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter= .N()$name != kd)  )+
      geom_node_point( shape = 23, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter = .N()$name == kd) )+
      geom_node_text(aes(label = name), size = 2) +
      coord_fixed() +
      scale_size_continuous( range = c(.5, 10), limits = c(0, 5), trans = 'exp')+
      scale_fill_gradient2(
        low = 'purple', mid = 'grey20', high = 'green', na.value = 'grey85',
        limits = c(-2.5,2.5) )+ #approx: range(omics$Pro_TE, na.rm = T)
      labs( title = 'All term genes in NW',
            subtitle = paste0('KD: ', kd, '\nTerm: ', term) )+
      theme_graph(background = 'white')
    ,
    ggraph(g2, layout = 'linear', circular = TRUE) +
            geom_edge_arc(alpha = .3, color = 'grey75') +
      geom_node_point( shape = 21, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter= .N()$name != kd)  )+
      geom_node_point( shape = 23, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter = .N()$name == kd) )+
      geom_node_text(aes(label = name), size = 2) +
      coord_fixed() +
      scale_size_continuous( range = c(.5, 10), limits = c(0, 5), trans = 'exp')+
      scale_fill_gradient2(
        low = 'purple', mid = 'grey20', high = 'green', na.value = 'grey85',
        limits = c(-2.5,2.5) )+ #approx: range(omics$Pro_TE, na.rm = T)
      labs( title = 'Term genes & KD neighbors in NW',
            subtitle = paste0('KD: ', kd, '\nTerm: ', term) )+
      theme_graph(background = 'white')
    ,
    ncol = 2
    
  )
}
```



# Enriched Biodomain terms

## Enriched terms by biodomain
```{r fig.width=15, fig.height=12}

ggplot(data = subset(enr.bd, Biodomain != 'none'), aes(NES, -log10(padj)))+
  geom_vline(xintercept = 1.7, lty = 2, lwd = .2, color = 'grey30')+
  geom_hline(yintercept = -log10(0.01), lty = 2, lwd = .2, color = 'grey30')+
  # geom_smooth(method = "lm", formula = y ~ poly(x, 2), lwd = .2)+
  geom_point(
    data = subset(enr.bd, padj > 0.05 & Biodomain != 'none'),
    shape = 21, size = .2, alpha = .3, color = 'grey20')+
  geom_point(
    data = subset(enr.bd, padj <= 0.05 & Biodomain != 'none'),
    shape = 21, color = 'grey50', alpha = .3, 
    aes(fill = color, size = size ))+
  scale_fill_identity()+
  theme(legend.position = 'top')+
  ggrepel::geom_label_repel(
    data = subset(enr.bd, padj < 0.01 & NES > 1.7 & Biodomain != 'none'),
    aes(label = str_trunc(pathway, 40, 'right',)),
    size = 2.5, alpha = .7, min.segment.length = 0, max.overlaps = 10
  )+
  facet_wrap(~Biodomain, scales = 'free')

```


## Enriched terms by subdomain {.tabset}
```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=15, fig.height=12}
tmp <- full_join( enr.bd, 
                  subdom %>% select(Biodomain, ID = GO_ID, Subdomain, TopSD),
                  by = c('Biodomain','ID')) %>% 
  group_by(Biodomain, Subdomain) %>% 
  mutate(sub_dom = pathway[TopSD == 1]) %>% 
  ungroup()

bd = unique(subdom$Biodomain)

for(i in 1:length(bd)) {
  cat("  \n###",  bd[i], "  \n")
  
  tmp1 <- tmp %>% filter(Biodomain == bd[i])
  
  p = ggplot(data = subset(tmp1, Biodomain != 'none'), aes(NES, -log10(padj)))+
    geom_vline(xintercept = 1.7, lty = 2, lwd = .2, color = 'grey30')+
    geom_hline(yintercept = -log10(0.01), lty = 2, lwd = .2, color = 'grey30')+
    # geom_smooth(method = "lm", formula = y ~ poly(x, 2), lwd = .2)+
    geom_point(
      data = subset(tmp1, padj > 0.05 & Biodomain != 'none'),
      shape = 21, size = .2, alpha = .3, color = 'grey20')+
    geom_point(
      data = subset(tmp1, padj <= 0.05 & Biodomain != 'none'),
      shape = 21, color = 'grey50', alpha = .3, 
      aes(fill = color, size = size ))+
    scale_fill_identity()+
    theme(legend.position = 'top')+
    ggrepel::geom_label_repel(
      data = subset(tmp1, padj < 0.01 & NES > 1.7 & Biodomain != 'none'),
      aes(label = str_trunc(pathway, 40, 'right',)),
      size = 2.5, alpha = .7, min.segment.length = 0, max.overlaps = 10
    )+
    facet_wrap(~sub_dom, scales = 'free')
  
  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
  
}

```
 

## Examine p-value & NES thresholding
```{r}
thresh = crossing(
  p = c(0.05, 0.01, 0.001, 1e-4, 1e-5, 1e-6),
  nes = quantile( enr.bd$NES[enr.bd$padj < 0.05], c(.2,.3,.4,.5,.6,.7,.8,.9), na.rm = T)
)

x = tibble()

for( bd in unique(enr.bd$Biodomain) ){
  n_GO = map_dbl(
    1:nrow(thresh), 
    ~ enr.bd %>% filter(Biodomain == bd, NES > thresh$nes[.x], padj <= thresh$p[.x]) %>% pull(ID) %>% unique() %>% length()
      )
  n_LE_genes = map_dbl(
    1:nrow(thresh), 
    ~ enr.bd %>% filter(Biodomain == bd, NES > thresh$nes[.x], padj <= thresh$p[.x]) %>% pull(leadingEdge_genes) %>% unlist() %>% unique() %>% length()
  )
  
  x <- tibble(
    bd = bd,
    n_GO = n_GO,
    n_LE_genes = n_LE_genes
  ) %>% 
    bind_cols( thresh, .) %>% 
    bind_rows( x, .)
}

thresh <- x %>% 
  left_join(., biodom %>% select(bd = Biodomain, abbr:color) %>% distinct(), by = 'bd') %>% 
  group_by(bd) %>% 
  mutate(
    pct_max_GO = n_GO / max(n_GO),
    pct_max_LE = n_LE_genes / max(n_LE_genes)
  ) 

```

Number of GO terms enriched at various thresholds  
```{r fig.width=10, fig.height=8}
ggplot(data = subset(thresh, bd!='none'), 
       aes( as.factor(signif(p, 2)), as.factor(signif(nes, 2)) ))+
  geom_point(aes(size = n_GO, fill = color), shape = 21, color = 'grey30', alpha = .9)+
  labs(x = 'p-adjust threshold', y = 'NES threshold')+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  scale_size_continuous( limits = c(1,max(thresh$n_GO[thresh$bd!='none'])) )+
  scale_fill_identity()+ 
  facet_wrap(~bd)
```

Number of leading edge genes (i.e. input to path trace) at various thresholds  
```{r fig.width=10, fig.height=8}
ggplot(data = subset(thresh, bd!='none'), 
       aes( as.factor(signif(p, 2)), as.factor(signif(nes, 2)) ))+
  geom_point(aes(size = n_LE_genes, fill = color), shape = 21, color = 'grey30', alpha = .9)+
  labs(x = 'p-adjust threshold', y = 'NES threshold')+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  scale_size_continuous( limits = c(1,max(thresh$n_LE_genes[thresh$bd!='none'])) )+
  scale_fill_identity()+ 
  facet_wrap(~bd)
```

Percent of maximum number of leading edge genes (i.e. input to path trace) at various thresholds  
```{r fig.width=10, fig.height=8}
ggplot(data = subset(thresh, bd!='none'), 
       aes( as.factor(signif(p, 2)), as.factor(signif(nes, 2)) ))+
  geom_point(aes(size = pct_max_LE, fill = color), shape = 21, color = 'grey30', alpha = .9)+
  labs(x = 'p-adjust threshold', y = 'NES threshold')+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  scale_size_continuous( limits = c(1e-200,1) )+
  scale_fill_identity()+ 
  facet_wrap(~bd)
```

# GO term NWs clustering

## JWiley sub-domains
### GO term overlap between sub-domains {.tabset}
```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=8, fig.height=6}

bd <- subdom$Biodomain %>% unique %>% sort 

# olap = tibble()

for(i in 1:length(bd)) {
  cat("  \n###",  bd[i], "  \n")
  
  sd = subdom %>% filter(Biodomain == bd[i]) %>% 
    group_by(Subdomain) %>% 
    mutate(sub_dom = GOterm_Name[TopSD == 1]) %>% 
    left_join(., biodom %>% select(GO_ID, symbol), by = 'GO_ID' ) %>% 
    unnest(symbol) %>% 
    group_by(Biodomain, Subdomain) %>% 
    summarise(terms = GO_ID %>% unique() %>% list())

  olap <- crossing(c = sd$Subdomain, b = sd$Subdomain) %>% 
    rowwise() %>% 
    mutate(
      n_c = sd %>% filter(Subdomain == c) %>% pull(terms) %>% unlist() %>% length() ,
      n_b = sd %>% filter(Subdomain == b) %>% pull(terms) %>% unlist() %>% length()
    ) %>% 
    group_by(c,b) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             sd %>% filter(Subdomain == c) %>% pull(terms) %>% unlist(),
             sd %>% filter(Subdomain == b) %>% pull(terms) %>% unlist()
             ))
           ) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(.keep = 'all', 
           pct_c = intersect / n_c,
           pct_b = intersect / n_b ) %>%
    ungroup() %>% 
    mutate(
      c = str_remove_all(c, '.graphml'),
      c = fct_reorder( as.factor(c), n_c),
      b = str_remove_all(b, '.graphml'),
      b = fct_reorder( as.factor(b), n_b)
    ) 
  
    p = #cowplot::plot_grid(
    
      ggplot(olap, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
        # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
        viridis::scale_fill_viridis("% Y", option = "C", direction = -1)+
        # scale_x_discrete(position = "top") +
        geom_text(aes(label = intersect ), size = 2.5) +
        labs(x='Sub-domain',y='Sub-domain', 
             title = bd[i],
             subtitle = 'Sub-domain GO terms')
      
      # ggplot(olap, aes(x = c, y = b)) +
      #   geom_tile(aes(fill=pct_c), alpha = .8) + theme_bw() +
      #   theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
      #   # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
      #   # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
      #   viridis::scale_fill_viridis("% Cluster", option = "C", direction = -1)+
      #   # scale_x_discrete(position = "top") +
      #   geom_text(aes(label = intersect ), size = 2.5) +
      #   labs(x='Louvian Cluster',y='Sub-domain'),
      # 
      # nrow = 1
      # )

  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
  
  }

```

### gene overlap between sub-domains {.tabset}
```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=8, fig.height=6}

bd <- subdom$Biodomain %>% unique %>% sort

# olap = tibble()

for(i in 1:length(bd)) {
  cat("  \n###",  bd[i], "  \n")
  
  sd = subdom %>% filter(Biodomain == bd[i]) %>% 
    group_by(Subdomain) %>% 
    mutate(sub_dom = GOterm_Name[TopSD == 1]) %>% 
    left_join(., biodom %>% select(GO_ID, symbol), by = 'GO_ID' ) %>% 
    unnest(symbol) %>% 
    group_by(Biodomain, Subdomain) %>% 
    summarise(genes = symbol %>% unique() %>% list())

  olap <- crossing(c = sd$Subdomain, b = sd$Subdomain) %>% 
    rowwise() %>% 
    mutate(
      n_c = sd %>% filter(Subdomain == c) %>% pull(genes) %>% unlist() %>% length() ,
      n_b = sd %>% filter(Subdomain == b) %>% pull(genes) %>% unlist() %>% length()
    ) %>% 
    group_by(c,b) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             sd %>% filter(Subdomain == c) %>% pull(genes) %>% unlist(),
             sd %>% filter(Subdomain == b) %>% pull(genes) %>% unlist()
             ))
           ) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(.keep = 'all', 
           pct_c = intersect / n_c,
           pct_b = intersect / n_b ) %>%
    ungroup() %>% 
    mutate(
      c = str_remove_all(c, '.graphml'),
      c = fct_reorder( as.factor(c), n_c),
      b = str_remove_all(b, '.graphml'),
      b = fct_reorder( as.factor(b), n_b)
    ) 
  
    p = #cowplot::plot_grid(
    
      ggplot(olap, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
        # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
        viridis::scale_fill_viridis("% Y", option = "C", direction = -1)+
        # scale_x_discrete(position = "top") +
        geom_text(aes(label = intersect ), size = 2.5) +
        labs(x='Sub-domain',y='Sub-domain', 
             title = bd[i],
             subtitle = 'Genes annotated to GO terms within sub-domain')
      
      # ggplot(olap, aes(x = c, y = b)) +
      #   geom_tile(aes(fill=pct_c), alpha = .8) + theme_bw() +
      #   theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
      #   # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
      #   # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
      #   viridis::scale_fill_viridis("% Cluster", option = "C", direction = -1)+
      #   # scale_x_discrete(position = "top") +
      #   geom_text(aes(label = intersect ), size = 2.5) +
      #   labs(x='Louvian Cluster',y='Sub-domain'),
      # 
      # nrow = 1
      # )

  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
  
  }

```

## enriched term network
### whole network
#### GO terms
```{r}
enr.nw.louvian <- igraph::cluster_louvain(enr.nw, weights = E(enr.nw)$kappa )

lclust <- tibble( clust = enr.nw.louvian$membership, terms = enr.nw.louvian$names) %>% 
   nest(.,cols = terms)

bd <- biodom %>% 
  select(Biodomain, GO_ID) %>% 
  nest(., cols = GO_ID) %>% 
  filter(!is.na(Biodomain))

olap <- crossing(c = lclust$clust, b = bd$Biodomain) %>% 
  rowwise() %>% 
  mutate(
    n_c = lclust %>% filter(clust == c) %>% pull(cols) %>% unlist() %>% unique() %>% length(),
    n_b = bd %>% filter(Biodomain == b) %>% pull(cols) %>% unlist() %>% unique() %>% length()
  ) %>% 
  group_by(c,b) %>% 
  mutate(.keep = 'all', 
         intersect = length(intersect(
           lclust %>% filter(clust == c) %>% pull(cols) %>% unlist(),
           bd %>% filter(Biodomain == b) %>% pull(cols) %>% unlist()
           ))
         ) %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(.keep = 'all', 
         pct_c = intersect / n_c,
         pct_b = intersect / n_b ) %>%
  ungroup() %>% 
  mutate(
    c = fct_reorder( as.factor(c), n_c),
    b = fct_reorder( as.factor(b), n_b)
  )


```

```{r fig.width=16, fig.height=6}

cowplot::plot_grid(
  
  ggplot(olap, aes(x = c, y = b)) +
    geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
    # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
    viridis::scale_fill_viridis("% Biodomain", option = "C", direction = -1)+
    # scale_x_discrete(position = "top") +
    geom_text(aes(label = intersect ), size = 2.5) +
    labs(x='Louvian Cluster',y='Biological Domain',
         title = 'Enr Term NW Louvian clusters',
         subtitle = 'GO term overlap with Biological domains'),
  
  ggplot(olap, aes(x = c, y = b)) +
    geom_tile(aes(fill=pct_c), alpha = .8) + theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
    # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
    viridis::scale_fill_viridis("% Cluster", option = "C", direction = -1)+
    # scale_x_discrete(position = "top") +
    geom_text(aes(label = intersect ), size = 2.5) +
    labs(x='Louvian Cluster',y='Biological Domain',
         title = 'Enr Term NW Louvian clusters',
         subtitle = 'GO term overlap with Biological domains'),
  
  nrow = 1
)


```

#### Genes annotated to terms
```{r}
enr.nw.louvian <- igraph::cluster_louvain(enr.nw, weights = E(enr.nw)$kappa )

lclust <- tibble( clust = enr.nw.louvian$membership, terms = enr.nw.louvian$names) %>% 
  left_join(., enr.bd %>% select(terms = ID, Biodomain, padj, NES, leadingEdge_genes) ) %>% 
  unnest(leadingEdge_genes) %>% 
  select(-NES, -padj) %>% 
  group_by(Biodomain, clust) %>% 
  summarise(terms = list(unique(terms)), genes = list(unique(leadingEdge_genes))) 

bd <- biodom %>% 
  select(Biodomain, GO_ID, genes = symbol) %>% 
  group_by(Biodomain) %>% 
  summarise(
    terms = list(unique(GO_ID)),
    genes = unlist(genes) %>% unique() %>% list()) %>% 
  filter(!is.na(Biodomain))

olap <- crossing(c = lclust$clust, b = bd$Biodomain) %>% 
  rowwise() %>% 
  mutate(
    n_c = lclust %>% filter(clust == c) %>% pull(genes) %>% unlist() %>% unique() %>% length(),
    n_b = bd %>% filter(Biodomain == b) %>% pull(genes) %>% unlist() %>% unique() %>% length()
  ) %>% 
  group_by(c,b) %>% 
  mutate(.keep = 'all', 
         intersect = length(intersect(
           lclust %>% filter(clust == c) %>% pull(genes) %>% unlist(),
           bd %>% filter(Biodomain == b) %>% pull(genes) %>% unlist()
           ))
         ) %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(.keep = 'all', 
         pct_c = intersect / n_c,
         pct_b = intersect / n_b ) %>%
  ungroup() %>% 
  mutate(
    c = fct_reorder( as.factor(c), n_c),
    b = fct_reorder( as.factor(b), n_b)
  )


```

```{r fig.width=16, fig.height=6}

cowplot::plot_grid(
  
  ggplot(olap, aes(x = c, y = b)) +
    geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
    # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
    viridis::scale_fill_viridis("% Biodomain", option = "C", direction = -1)+
    # scale_x_discrete(position = "top") +
    geom_text(aes(label = intersect ), size = 2.5) +
    labs(x='Louvian Cluster',y='Biological Domain',
         title = 'Enr Term NW Louvian clusters',
         subtitle = 'GO term overlap with Biological domains'),
  
  ggplot(olap, aes(x = c, y = b)) +
    geom_tile(aes(fill=pct_c), alpha = .8) + theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
    # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
    viridis::scale_fill_viridis("% Cluster", option = "C", direction = -1)+
    # scale_x_discrete(position = "top") +
    geom_text(aes(label = intersect ), size = 2.5) +
    labs(x='Louvian Cluster',y='Biological Domain',
         title = 'Enr Term NW Louvian clusters',
         subtitle = 'GO term overlap with Biological domains'),
  
  nrow = 1
)


```


### by biodomain, terms {.tabset}
cluster sub-networks defined by biological domain annotation  
```{r}
x <- tibble(
  bd = vertex_attr_names(enr.nw)[8:27],
  n_subclust = NA_real_,
  subclust = list(NA)
)

for(i in 1:nrow(x)){
  rm_idx <- which( vertex_attr(enr.nw, x$bd[i]) != 1 ) 
  tmp <- delete_vertices( enr.nw, rm_idx )
  subclust <- igraph::cluster_louvain(tmp, weights = E(tmp)$kappa )
  x$n_subclust[i] <- subclust$membership %>% unique %>% length
  x$subclust[[i]] <- tibble( id = subclust$names, clust = subclust$membership ) %>% 
    left_join(., biodom %>% select(id = GO_ID, GOterm_Name), by = 'id') 
}

i = which(x$bd == 'none')
x$subclust[[i]] <- x$subclust[[i]] %>% 
  left_join(., enr.bd %>% select(id = ID, name = pathway, size), by = 'id')

enr.nw.bd.subclusters <- x
```

Compare with sub-domain annotations from Jesse  
```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=16, fig.height=6}
bd = unique(subdom$Biodomain)

for(i in 1:length(bd)) {
  cat("  \n####",  bd[i], "  \n")
  
  sd = subdom %>% filter(Biodomain == bd[i])
  
  if( nrow(enr.nw.bd.subclusters[which(enr.nw.bd.subclusters$bd == bd[i]),]) == 0 ){ next }
  
  lc = enr.nw.bd.subclusters[which(enr.nw.bd.subclusters$bd == bd[i]),] %>% pull(subclust) %>% .[[1]] 
  
  olap <- crossing(c = unique(lc$clust), b = unique(sd$Subdomain) ) %>% 
    rowwise() %>% 
    mutate(
      n_c = lc %>% filter( clust == as.numeric(c) ) %>% pull(id) %>% unique() %>% length(),
      n_b = sd %>% filter( Subdomain == as.numeric(b) ) %>% pull(GO_ID) %>% unique() %>% length()
    ) %>% 
    group_by(c,b) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             lc %>% filter( clust == as.numeric(c) ) %>% pull(id),
             sd %>% filter( Subdomain == as.numeric(b) ) %>% pull(GO_ID)
             ))
           ) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(.keep = 'all', 
           pct_c = intersect / n_c,
           pct_b = intersect / n_b ) %>%
    ungroup() %>% 
    mutate(
      c = fct_reorder( as.factor(c), n_c),
      b = fct_reorder( as.factor(b), n_b)
    )

  p = cowplot::plot_grid(
    
      ggplot(olap, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
        # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
        viridis::scale_fill_viridis("% Subdomain", option = "C", direction = -1)+
        # scale_x_discrete(position = "top") +
        geom_text(aes(label = intersect ), size = 2.5) +
        labs(x='Louvian Cluster',y='Sub-domain',
             title = bd[i],
             subtitle = 'GO terms in Enr Term NW Louvian Clusters vs Subdomains'),
      
      ggplot(olap, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_c), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
        # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
        viridis::scale_fill_viridis("% Cluster", option = "C", direction = -1)+
        # scale_x_discrete(position = "top") +
        geom_text(aes(label = intersect ), size = 2.5) +
        labs(x='Louvian Cluster',y='Sub-domain',
             title = bd[i],
             subtitle = 'GO terms in Enr Term NW Louvian Clusters vs Subdomains'),
      
      nrow = 1
      )

  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
  
}

```

### by biodomain, genes {.tabset}
cluster sub-networks defined by biological domain annotation  
```{r}
x <- tibble(
  bd = vertex_attr_names(enr.nw)[8:27],
  n_subclust = NA_real_,
  subclust = list(NA)
)

for(i in 1:nrow(x)){
  rm_idx <- which( vertex_attr(enr.nw, x$bd[i]) != 1 ) 
  tmp <- delete_vertices( enr.nw, rm_idx )
  subclust <- igraph::cluster_louvain(tmp, weights = E(tmp)$kappa )
  x$n_subclust[i] <- subclust$membership %>% unique %>% length
  x$subclust[[i]] <- tibble( id = subclust$names, clust = subclust$membership ) %>% 
    left_join(., biodom %>% select(id = GO_ID, GOterm_Name, symbol), by = 'id') 
}

i = which(x$bd == 'none')
x$subclust[[i]] <- x$subclust[[i]] %>% 
  left_join(., enr.bd %>% select(id = ID, name = pathway, size), by = 'id')

enr.nw.bd.subclusters <- x
```

Compare with sub-domain annotations from Jesse  
```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=16, fig.height=6}
bd = unique(subdom$Biodomain)

for(i in 1:length(bd)) {
  cat("  \n####",  bd[i], "  \n")
  
  sd = subdom %>% filter(Biodomain == bd[i]) %>% 
    group_by(Subdomain) %>% 
    mutate(sub_dom = GOterm_Name[TopSD == 1]) %>% 
    left_join(., biodom %>% select(GO_ID, symbol), by = 'GO_ID' ) %>% 
    unnest(symbol) %>% 
    group_by(Biodomain, Subdomain) %>% 
    summarise(symbol = symbol %>% unique() %>% list())
  
  if( nrow(enr.nw.bd.subclusters[which(enr.nw.bd.subclusters$bd == bd[i]),]) == 0 ){ next }
  
  lc = enr.nw.bd.subclusters[which(enr.nw.bd.subclusters$bd == bd[i]),] %>% 
    pull(subclust) %>% .[[1]] %>% 
    group_by(clust) %>% 
    summarise(symbol = unlist(symbol) %>% unique() %>% list())
  
  olap <- crossing(c = unique(lc$clust), b = unique(sd$Subdomain) ) %>% 
    rowwise() %>% 
    mutate(
      n_c = lc %>% filter( clust == as.numeric(c) ) %>% pull(symbol) %>% unlist() %>% unique() %>% length(),
      n_b = sd %>% filter( Subdomain == as.numeric(b) ) %>% pull(symbol) %>% unlist() %>% unique() %>% length()
    ) %>% 
    group_by(c,b) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             lc %>% filter( clust == as.numeric(c) ) %>% pull(symbol) %>% unlist() %>% unique(),
             sd %>% filter( Subdomain == as.numeric(b) ) %>% pull(symbol) %>% unlist() %>% unique()
             ))
           ) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(.keep = 'all', 
           pct_c = intersect / n_c,
           pct_b = intersect / n_b ) %>%
    ungroup() %>% 
    mutate(
      c = fct_reorder( as.factor(c), n_c),
      b = fct_reorder( as.factor(b), n_b)
    )

  p = cowplot::plot_grid(
    
      ggplot(olap, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
        # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
        viridis::scale_fill_viridis("% Subdomain", option = "C", direction = -1)+
        # scale_x_discrete(position = "top") +
        geom_text(aes(label = intersect ), size = 2.5) +
        labs(x='Louvian Cluster',y='Sub-domain',
             title = bd[i],
             subtitle = 'Genes from Enr Term NW Louvian Clusters vs Subdomains'),
      
      ggplot(olap, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_c), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
        # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
        viridis::scale_fill_viridis("% Cluster", option = "C", direction = -1)+
        # scale_x_discrete(position = "top") +
        geom_text(aes(label = intersect ), size = 2.5) +
        labs(x='Louvian Cluster',y='Sub-domain',
             title = bd[i],
             subtitle = 'Genes from Enr Term NW Louvian Clusters vs Subdomains'),
      
      nrow = 1
      )

  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
  
}

```
## term annotation network
### whole network
#### GO terms
```{r}
biodom.nw.louvian <- igraph::cluster_louvain(biodom.nw, weights = E(biodom.nw)$kappa )

lclust <- tibble( clust = biodom.nw.louvian$membership, terms = biodom.nw.louvian$names) %>% 
   nest(.,cols = terms)

bd <- biodom %>% 
  select(Biodomain, GO_ID) %>% 
  nest(., cols = GO_ID) %>% 
  filter(!is.na(Biodomain))

olap <- crossing(c = lclust$clust, b = bd$Biodomain) %>% 
  rowwise() %>% 
  mutate(
    n_c = lclust %>% filter(clust == c) %>% pull(cols) %>% unlist() %>% unique() %>% length(),
    n_b = bd %>% filter(Biodomain == b) %>% pull(cols) %>% unlist() %>% unique() %>% length()
  ) %>% 
  group_by(c,b) %>% 
  mutate(.keep = 'all', 
         intersect = length(intersect(
           lclust %>% filter(clust == c) %>% pull(cols) %>% unlist(),
           bd %>% filter(Biodomain == b) %>% pull(cols) %>% unlist()
           ))
         ) %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(.keep = 'all', 
         pct_c = intersect / n_c,
         pct_b = intersect / n_b ) %>%
  ungroup() %>% 
  mutate(
    c = fct_reorder( as.factor(c), n_c),
    b = fct_reorder( as.factor(b), n_b)
  )


```

```{r fig.width=16, fig.height=6}

cowplot::plot_grid(
  
  ggplot(olap, aes(x = c, y = b)) +
    geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
    # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
    viridis::scale_fill_viridis("% Biodomain", option = "C", direction = -1)+
    # scale_x_discrete(position = "top") +
    geom_text(aes(label = intersect ), size = 2.5) +
    labs(x='Louvian Cluster',y='Biological Domain',
         title = 'Term Annotation NW Louvian clusters',
         subtitle = 'GO term overlap with Biological domains'),
  
  ggplot(olap, aes(x = c, y = b)) +
    geom_tile(aes(fill=pct_c), alpha = .8) + theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
    # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
    viridis::scale_fill_viridis("% Cluster", option = "C", direction = -1)+
    # scale_x_discrete(position = "top") +
    geom_text(aes(label = intersect ), size = 2.5) +
    labs(x='Louvian Cluster',y='Biological Domain',
         title = 'Term Annotation NW Louvian clusters',
         subtitle = 'GO term overlap with Biological domains'),
  
  nrow = 1
)


```

#### Genes annotated to terms
```{r}
biodom.nw.louvian <- igraph::cluster_louvain(biodom.nw, weights = E(biodom.nw)$kappa )

lclust <- tibble( clust = biodom.nw.louvian$membership, terms = biodom.nw.louvian$names) %>% 
  left_join(., enr.bd %>% select(terms = ID, Biodomain, padj, NES, leadingEdge_genes) ) %>% 
  unnest(leadingEdge_genes) %>% 
  select(-NES, -padj) %>% 
  group_by(Biodomain, clust) %>% 
  summarise(terms = list(unique(terms)), genes = list(unique(leadingEdge_genes))) 

bd <- biodom %>% 
  select(Biodomain, GO_ID, genes = symbol) %>% 
  group_by(Biodomain) %>% 
  summarise(
    terms = list(unique(GO_ID)),
    genes = unlist(genes) %>% unique() %>% list()) %>% 
  filter(!is.na(Biodomain))

olap <- crossing(c = lclust$clust, b = bd$Biodomain) %>% 
  rowwise() %>% 
  mutate(
    n_c = lclust %>% filter(clust == c) %>% pull(genes) %>% unlist() %>% unique() %>% length(),
    n_b = bd %>% filter(Biodomain == b) %>% pull(genes) %>% unlist() %>% unique() %>% length()
  ) %>% 
  group_by(c,b) %>% 
  mutate(.keep = 'all', 
         intersect = length(intersect(
           lclust %>% filter(clust == c) %>% pull(genes) %>% unlist(),
           bd %>% filter(Biodomain == b) %>% pull(genes) %>% unlist()
           ))
         ) %>% 
  ungroup() %>% 
  rowwise() %>% 
  mutate(.keep = 'all', 
         pct_c = intersect / n_c,
         pct_b = intersect / n_b ) %>%
  ungroup() %>% 
  mutate(
    c = fct_reorder( as.factor(c), n_c),
    b = fct_reorder( as.factor(b), n_b)
  )


```

```{r fig.width=16, fig.height=6}

cowplot::plot_grid(
  
  ggplot(olap, aes(x = c, y = b)) +
    geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
    # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
    viridis::scale_fill_viridis("% Biodomain", option = "C", direction = -1)+
    # scale_x_discrete(position = "top") +
    geom_text(aes(label = intersect ), size = 2.5) +
    labs(x='Louvian Cluster',y='Biological Domain',
         title = 'Enr Term NW Louvian clusters',
         subtitle = 'GO term overlap with Biological domains'),
  
  ggplot(olap, aes(x = c, y = b)) +
    geom_tile(aes(fill=pct_c), alpha = .8) + theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
    # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
    viridis::scale_fill_viridis("% Cluster", option = "C", direction = -1)+
    # scale_x_discrete(position = "top") +
    geom_text(aes(label = intersect ), size = 2.5) +
    labs(x='Louvian Cluster',y='Biological Domain',
         title = 'Enr Term NW Louvian clusters',
         subtitle = 'GO term overlap with Biological domains'),
  
  nrow = 1
)


```
### by biodomain, terms {.tabset}
cluster sub-networks defined by biological domain annotation  
```{r}
x <- tibble(
  bd = vertex_attr_names(biodom.nw)[9:27],
  n_subclust = NA_real_,
  subclust = list(NA)
)

for(i in 1:nrow(x)){
  rm_idx <- which( vertex_attr(biodom.nw, x$bd[i]) != 1 ) 
  tmp <- delete_vertices( biodom.nw, rm_idx )
  subclust <- igraph::cluster_louvain(tmp, weights = E(tmp)$kappa )
  x$subclust[[i]] <- tibble( id = subclust$names, clust = subclust$membership ) %>% 
    left_join(., biodom %>% select(id = GO_ID, GOterm_Name), by = 'id') %>% 
    filter(!is.na(GOterm_Name))
  x$n_subclust[i] <- x$subclust[[i]]$clust %>% unique %>% length
}

biodom.nw.bd.subclusters <- x
```

Compare with sub-domain annotations from Jesse  
```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=16, fig.height=6}
bd = unique(subdom$Biodomain)

for(i in 1:length(bd)) {
  cat("  \n####",  bd[i], "  \n")
  
  sd = subdom %>% filter(Biodomain == bd[i])
  
  if( nrow(biodom.nw.bd.subclusters[which(biodom.nw.bd.subclusters$bd == bd[i]),]) == 0 ){ next }
  
  lc = biodom.nw.bd.subclusters[which(biodom.nw.bd.subclusters$bd == bd[i]),] %>% pull(subclust) %>% .[[1]] 
  
  olap <- crossing(c = unique(lc$clust), b = unique(sd$Subdomain) ) %>% 
    rowwise() %>% 
    mutate(
      n_c = lc %>% filter( clust == as.numeric(c) ) %>% pull(id) %>% unique() %>% length(),
      n_b = sd %>% filter( Subdomain == as.numeric(b) ) %>% pull(GO_ID) %>% unique() %>% length()
    ) %>% 
    group_by(c,b) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             lc %>% filter( clust == as.numeric(c) ) %>% pull(id),
             sd %>% filter( Subdomain == as.numeric(b) ) %>% pull(GO_ID)
             ))
           ) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(.keep = 'all', 
           pct_c = intersect / n_c,
           pct_b = intersect / n_b ) %>%
    ungroup() %>% 
    mutate(
      c = fct_reorder( as.factor(c), n_c),
      b = fct_reorder( as.factor(b), n_b)
    )

  p = cowplot::plot_grid(
    
      ggplot(olap, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
        # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
        viridis::scale_fill_viridis("% Subdomain", option = "C", direction = -1)+
        # scale_x_discrete(position = "top") +
        geom_text(aes(label = intersect ), size = 2.5) +
        labs(x='Louvian Cluster',y='Sub-domain',
             title = bd[i],
             subtitle = 'GO terms in Term Annotation NW Louvian Clusters vs Subdomains'),
      
      ggplot(olap, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_c), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
        # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
        viridis::scale_fill_viridis("% Cluster", option = "C", direction = -1)+
        # scale_x_discrete(position = "top") +
        geom_text(aes(label = intersect ), size = 2.5) +
        labs(x='Louvian Cluster',y='Sub-domain',
             title = bd[i],
             subtitle = 'GO terms in Term Annotation NW Louvian Clusters vs Subdomains'),
      
      nrow = 1
      )

  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
  
}

```

### by biodomain, genes {.tabset}
cluster sub-networks defined by biological domain annotation  
```{r}
x <- tibble(
  bd = vertex_attr_names(biodom.nw)[9:27],
  n_subclust = NA_real_,
  subclust = list(NA)
)

for(i in 1:nrow(x)){
  rm_idx <- which( vertex_attr(biodom.nw, x$bd[i]) != 1 ) 
  tmp <- delete_vertices( biodom.nw, rm_idx )
  subclust <- igraph::cluster_louvain(tmp, weights = E(tmp)$kappa )
  x$subclust[[i]] <- tibble( id = subclust$names, clust = subclust$membership ) %>% 
    left_join(., biodom %>% select(id = GO_ID, GOterm_Name, symbol), by = 'id') %>% 
    filter(!is.na(GOterm_Name))
  x$n_subclust[i] <- x$subclust[[i]]$clust %>% unique %>% length
}

biodom.nw.bd.subclusters <- x
```

Compare with sub-domain annotations from Jesse  
```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=16, fig.height=6}
bd = unique(subdom$Biodomain)

for(i in 1:length(bd)) {
  cat("  \n####",  bd[i], "  \n")
  
  sd = subdom %>% filter(Biodomain == bd[i]) %>% 
    group_by(Subdomain) %>% 
    mutate(sub_dom = GOterm_Name[TopSD == 1]) %>% 
    left_join(., biodom %>% select(GO_ID, symbol), by = 'GO_ID' ) %>% 
    unnest(symbol) %>% 
    group_by(Biodomain, Subdomain) %>% 
    summarise(symbol = symbol %>% unique() %>% list())
  
  if( nrow(biodom.nw.bd.subclusters[which(biodom.nw.bd.subclusters$bd == bd[i]),]) == 0 ){ next }
  
  lc = biodom.nw.bd.subclusters[which(biodom.nw.bd.subclusters$bd == bd[i]),] %>% 
    pull(subclust) %>% .[[1]] %>% 
    group_by(clust) %>% 
    summarise(symbol = unlist(symbol) %>% unique() %>% list())
  
  olap <- crossing(c = unique(lc$clust), b = unique(sd$Subdomain) ) %>% 
    rowwise() %>% 
    mutate(
      n_c = lc %>% filter( clust == as.numeric(c) ) %>% pull(symbol) %>% unlist() %>% unique() %>% length(),
      n_b = sd %>% filter( Subdomain == as.numeric(b) ) %>% pull(symbol) %>% unlist() %>% unique() %>% length()
    ) %>% 
    group_by(c,b) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             lc %>% filter( clust == as.numeric(c) ) %>% pull(symbol) %>% unlist() %>% unique(),
             sd %>% filter( Subdomain == as.numeric(b) ) %>% pull(symbol) %>% unlist() %>% unique()
             ))
           ) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(.keep = 'all', 
           pct_c = intersect / n_c,
           pct_b = intersect / n_b ) %>%
    ungroup() %>% 
    mutate(
      c = fct_reorder( as.factor(c), n_c),
      b = fct_reorder( as.factor(b), n_b)
    )

  p = cowplot::plot_grid(
    
      ggplot(olap, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
        # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
        viridis::scale_fill_viridis("% Subdomain", option = "C", direction = -1)+
        # scale_x_discrete(position = "top") +
        geom_text(aes(label = intersect ), size = 2.5) +
        labs(x='Louvian Cluster',y='Sub-domain',
             title = bd[i],
             subtitle = 'Genes from Term Annotation NW Louvian Clusters vs Subdomains'),
      
      ggplot(olap, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_c), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
        # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
        viridis::scale_fill_viridis("% Cluster", option = "C", direction = -1)+
        # scale_x_discrete(position = "top") +
        geom_text(aes(label = intersect ), size = 2.5) +
        labs(x='Louvian Cluster',y='Sub-domain',
             title = bd[i],
             subtitle = 'Genes from Term Annotation NW Louvian Clusters vs Subdomains'),
      
      nrow = 1
      )

  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
  
}

```

## term annotation network -- filtered for kappa

### by biodomain, terms {.tabset}
cluster sub-networks defined by biological domain annotation  
```{r}
biodom.nw.bd.subclusters <- tibble()

for(j in c(0.3, 0.5, 0.7, 0.9, 0.95)){
  
  red.biodom.nw <- delete.edges(biodom.nw, E(biodom.nw)[E(biodom.nw)$kappa < j])

  x <- tibble(
    bd = vertex_attr_names(red.biodom.nw)[9:27],
    kappa = j,
    n_subclust = NA_real_,
    subclust = list(NA)
  )
  
  for(i in 1:nrow(x)){
    rm_idx <- which( vertex_attr(red.biodom.nw, x$bd[i]) != 1 ) 
    tmp <- delete_vertices( red.biodom.nw, rm_idx )
    subclust <- igraph::cluster_louvain(tmp, weights = E(tmp)$kappa )
    x$subclust[[i]] <- tibble( id = subclust$names, clust = subclust$membership ) %>% 
      left_join(., biodom %>% select(id = GO_ID, GOterm_Name, n_symbol), by = 'id') %>% 
      filter(!is.na(GOterm_Name)) %>% 
      group_by(clust) %>% 
      arrange(desc(n_symbol), .by_group = T) %>% 
      ungroup()
    x$n_subclust[i] <- x$subclust[[i]]$clust %>% unique %>% length
  }
  
  biodom.nw.bd.subclusters <- bind_rows(biodom.nw.bd.subclusters, x)
  
}

```

```{r warning=FALSE}
bd = biodom.nw.bd.subclusters %>% select(bd, kappa) %>% 
  filter(bd %in% subdom$Biodomain)

olap = tibble()

for(i in 1:nrow(bd)) {
  
  x = bd$bd[i]
  k = bd$kappa[i]
  
  sd = subdom %>% filter(Biodomain == x)
  
  lc = biodom.nw.bd.subclusters %>% filter(bd == x, kappa == k)
  
  if( nrow(lc$subclust[[1]]) == 0 ){ next }
  
  lc = lc %>% pull(subclust) %>% .[[1]] 
  
  olap <- crossing(c = unique(lc$clust), b = unique(sd$Subdomain) ) %>% 
    rowwise() %>% 
    mutate(
      n_c = lc %>% filter( clust == as.numeric(c) ) %>% pull(id) %>% unique() %>% length(),
      n_b = sd %>% filter( Subdomain == as.numeric(b) ) %>% pull(GO_ID) %>% unique() %>% length()
    ) %>% 
    group_by(c,b) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             lc %>% filter( clust == as.numeric(c) ) %>% pull(id),
             sd %>% filter( Subdomain == as.numeric(b) ) %>% pull(GO_ID)
             ))
           ) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(.keep = 'all', 
           pct_c = intersect / n_c,
           pct_b = intersect / n_b ) %>%
    ungroup() %>% 
    mutate(
      c = fct_reorder( as.factor(c), n_c),
      b = fct_reorder( as.factor(b), n_b),
      biodom = x,
      kappa = k
    ) %>% 
    bind_rows(olap, .)
}
```


Compare with sub-domain annotations from Jesse  
```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=5, fig.height=12}

bd = biodom.nw.bd.subclusters %>% select(bd) %>% 
  filter(bd %in% subdom$Biodomain) %>% 
  distinct()

for(i in 1:nrow(bd)) {

  cat("  \n####",  bd$bd[i], "  \n")

  tmp <- olap %>% filter(biodom == bd$bd[i]) 
  
  p = ggplot(tmp, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        viridis::scale_fill_viridis("% Subdomain", option = "C", direction = -1)+
        geom_text(aes(label = intersect ), size = 2.5) +
        facet_wrap(~kappa, scales = 'free', ncol =1)+
        labs(x='Louvian Cluster',y='Sub-domain',
             title = bd$bd[i],
             subtitle = 'Terms in sub-domain vs\nclusters of annotation network, filtered by edge kappa')
      
  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
  
}

```

### by biodomain, genes {.tabset}
cluster sub-networks defined by biological domain annotation   
```{r}
biodom.nw.bd.subclusters <- tibble()

for(j in c(0.3, 0.5, 0.7, 0.9, 0.95)){
  
  red.biodom.nw <- delete.edges(biodom.nw, E(biodom.nw)[E(biodom.nw)$kappa < j])

  x <- tibble(
    bd = vertex_attr_names(red.biodom.nw)[9:27],
    kappa = j,
    n_subclust = NA_real_,
    subclust = list(NA)
  )
  
  for(i in 1:nrow(x)){
    rm_idx <- which( vertex_attr(red.biodom.nw, x$bd[i]) != 1 ) 
    tmp <- delete_vertices( red.biodom.nw, rm_idx )
    subclust <- igraph::cluster_louvain(tmp, weights = E(tmp)$kappa )
    x$subclust[[i]] <- tibble( id = subclust$names, clust = subclust$membership ) %>% 
      left_join(., biodom %>% select(id = GO_ID, GOterm_Name, n_symbol, symbol), by = 'id') %>% 
      filter(!is.na(GOterm_Name)) %>% 
      group_by(clust) %>% 
      arrange(desc(n_symbol), .by_group = T) %>% 
      ungroup()
    x$n_subclust[i] <- x$subclust[[i]]$clust %>% unique %>% length
  }
  
  biodom.nw.bd.subclusters <- bind_rows(biodom.nw.bd.subclusters, x)
  
}

```

```{r message=FALSE}
bd = biodom.nw.bd.subclusters %>% select(bd, kappa) %>% 
  filter(bd %in% subdom$Biodomain)

olap = tibble()

for(i in 1:nrow(bd)) {
  
  x = bd$bd[i]
  k = bd$kappa[i]
  
  sd = subdom %>% filter(Biodomain == x) %>% 
    group_by(Subdomain) %>% 
    mutate(sub_dom = GOterm_Name[TopSD == 1]) %>% 
    left_join(., biodom %>% select(GO_ID, symbol), by = 'GO_ID' ) %>% 
    unnest(symbol) %>% 
    group_by(Biodomain, Subdomain) %>% 
    summarise(symbol = symbol %>% unique() %>% list())
  
  lc = biodom.nw.bd.subclusters %>% filter(bd == x, kappa == k)
  
  if( nrow(lc$subclust[[1]]) == 0 ){ next }
  
  lc = lc %>% pull(subclust) %>% .[[1]] %>% 
    group_by(clust) %>% 
    summarise(symbol = unlist(symbol) %>% unique() %>% list())
  
  olap <- crossing(c = unique(lc$clust), b = unique(sd$Subdomain) ) %>% 
    rowwise() %>% 
    mutate(
      n_c = lc %>% filter( clust == as.numeric(c) ) %>% pull(symbol) %>% unlist() %>% unique() %>% length(),
      n_b = sd %>% filter( Subdomain == as.numeric(b) ) %>% pull(symbol) %>% unlist() %>% unique() %>% length()
    ) %>% 
    group_by(c,b) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             lc %>% filter( clust == as.numeric(c) ) %>% pull(symbol) %>% unlist() %>% unique(),
             sd %>% filter( Subdomain == as.numeric(b) ) %>% pull(symbol) %>% unlist() %>% unique()
             ))
           ) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(.keep = 'all', 
           pct_c = intersect / n_c,
           pct_b = intersect / n_b ) %>%
    ungroup() %>% 
    mutate(
      c = fct_reorder( as.factor(c), n_c),
      b = fct_reorder( as.factor(b), n_b),
      biodom = x,
      kappa = k
    ) %>% 
    bind_rows(olap, .)
}

```


Compare with sub-domain annotations from Jesse  
```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=5, fig.height=12}

bd = biodom.nw.bd.subclusters %>% select(bd) %>% 
  filter(bd %in% subdom$Biodomain) %>% 
  distinct()

for(i in 1:nrow(bd)) {

  cat("  \n####",  bd$bd[i], "  \n")

  tmp <- olap %>% filter(biodom == bd$bd[i]) 
  
  p = ggplot(tmp, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        viridis::scale_fill_viridis("% Subdomain", option = "C", direction = -1)+
        geom_text(aes(label = intersect ), size = 2.5) +
        facet_wrap(~kappa, scales = 'free', ncol =1)+
        labs(x='Louvian Cluster',y='Sub-domain',
             title = bd$bd[i],
             subtitle = 'Genes in sub-domain vs\nclusters of annotation network, filtered by edge kappa')
      
  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
  
}

```

# Biodomain NW louvian clustering
Pull Rohit's communities from synapse  
```{r message=FALSE}
synLogin()

synID <- 'syn52223172'
synDir <- synGetChildren(synID)$asList() %>% tibble(f = .) %>% unnest_wider(f) %>% mutate(parent = synID)
synDir <- map_dfr(
  1:nrow(synDir),
  ~ synGetChildren(synDir$id[.x])$asList() %>% tibble(f = .) %>% unnest_wider(f) %>% mutate(parent = synDir$name[.x])
  ) %>% 
  mutate(bd_abbr = str_split_fixed(name, '_', 2) %>% .[,1]) 

x = tibble( biodom = biodom$Biodomain %>% unique() %>% sort() %>% str_subset('DNA Repair', negate = T), 
            bd_abbr = synDir$bd_abbr %>% unique)

synDir <- left_join(synDir, x, by = 'bd_abbr') %>% 
  select(biodom, name, id) %>% 
  rowwise() %>% 
  mutate(
    graph = synGet(id) %>% .$path %>% read.graph(., format = 'graphml') %>% list(),
    nodes = tibble( na = vertex.attributes(graph) ) %>% 
      t() %>% as_tibble(rownames = NA, .name_repair = 'unique') %>% unnest(everything()) %>%
      rename_with(., ~names(vertex.attributes(graph)), everything()) %>% list()
      # V(.) %>% names() %>% list()
  ) %>% 
  select(-graph)

nw.clust <- synDir; rm(synDir, synID)
```

## between cluster overlap   
```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=15, fig.height=12 }

bd <- nw.clust$biodom %>% unique %>% sort
olap = tibble()
for(i in 1:length(bd)) {
  # cat("  \n###",  bd[i], "  \n")
  
  tmp <- nw.clust %>% filter(biodom == bd[i])
  
  olap <- crossing(c = tmp$name, b = tmp$name) %>% 
    rowwise() %>% 
    mutate(
      n_c = tmp %>% filter(name == c) %>% pull(nodes) %>% .[[1]] %>% nrow() ,
      n_b = tmp %>% filter(name == b) %>% pull(nodes) %>% .[[1]] %>% nrow() 
    ) %>% 
    group_by(c,b) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             tmp %>% filter(name == c) %>% pull(nodes) %>% .[[1]] %>% .$name,
             tmp %>% filter(name == b) %>% pull(nodes) %>% .[[1]] %>% .$name
             ))
           ) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(.keep = 'all', 
           pct_c = intersect / n_c,
           pct_b = intersect / n_b ) %>%
    ungroup() %>% 
    mutate(
      c = str_remove_all(c, '.graphml'),
      c = fct_reorder( as.factor(c), n_c),
      b = str_remove_all(b, '.graphml'),
      b = fct_reorder( as.factor(b), n_b),
      bd = bd[i]
    ) %>% 
    bind_rows(olap,.)
  }

```

```{r fig.width=12, fig.height=10}
ggplot(olap, aes(x = c, y = b)) +
  geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  viridis::scale_fill_viridis("% x", option = "C", direction = -1)+
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  facet_wrap(~bd, scales = 'free')
```

## comparison with sub-domains {.tabset}
```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=16, fig.height=6}

bd <- nw.clust$biodom %>% unique %>% sort %>% 
  .[. %in% subdom$Biodomain]

# olap = tibble()

for(i in 1:length(bd)) {
  cat("  \n###",  bd[i], "  \n")
  
  sd = subdom %>% filter(Biodomain == bd[i]) %>% 
    group_by(Subdomain) %>% 
    mutate(sub_dom = GOterm_Name[TopSD == 1]) %>% 
    left_join(., biodom %>% select(GO_ID, symbol), by = 'GO_ID' ) %>% 
    unnest(symbol) %>% 
    group_by(Biodomain, Subdomain) %>% 
    summarise(genes = symbol %>% unique() %>% list())

  lc = nw.clust %>% filter(biodom ==  bd[i])
  
  olap <- crossing(c = lc$name, b = sd$Subdomain) %>% 
    rowwise() %>% 
    mutate(
      n_c = lc %>% filter(name == c) %>% pull(nodes) %>% .[[1]] %>% nrow() ,
      n_b = sd %>% filter(Subdomain == b) %>% pull(genes) %>% unlist() %>% length()
    ) %>% 
    group_by(c,b) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             lc %>% filter(name == c) %>% pull(nodes) %>% .[[1]] %>% .$name,
             sd %>% filter(Subdomain == b) %>% pull(genes) %>% unlist()
             ))
           ) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(.keep = 'all', 
           pct_c = intersect / n_c,
           pct_b = intersect / n_b ) %>%
    ungroup() %>% 
    mutate(
      c = str_remove_all(c, '.graphml'),
      c = fct_reorder( as.factor(c), n_c),
      b = str_remove_all(b, '.graphml'),
      b = fct_reorder( as.factor(b), n_b)
    ) 
  
    p = cowplot::plot_grid(
    
      ggplot(olap, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
        # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
        viridis::scale_fill_viridis("% Subdomain", option = "C", direction = -1)+
        # scale_x_discrete(position = "top") +
        geom_text(aes(label = intersect ), size = 2.5) +
        labs(x='Louvian Cluster',y='Sub-domain'),
      
      ggplot(olap, aes(x = c, y = b)) +
        geom_tile(aes(fill=pct_c), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
        # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
        viridis::scale_fill_viridis("% Cluster", option = "C", direction = -1)+
        # scale_x_discrete(position = "top") +
        geom_text(aes(label = intersect ), size = 2.5) +
        labs(x='Louvian Cluster',y='Sub-domain'),
      
      nrow = 1
      )

  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
  
  }

```

## comparison with term NW based clusters {.tabset}
```{r}
biodom.nw.bd.subclusters <- tibble()

for(j in c(0.3, 0.5, 0.7, 0.9, 0.95)){
  
  red.biodom.nw <- delete.edges(biodom.nw, E(biodom.nw)[E(biodom.nw)$kappa < j])

  x <- tibble(
    bd = vertex_attr_names(red.biodom.nw)[9:27],
    kappa = j,
    n_subclust = NA_real_,
    subclust = list(NA)
  )
  
  for(i in 1:nrow(x)){
    rm_idx <- which( vertex_attr(red.biodom.nw, x$bd[i]) != 1 ) 
    tmp <- delete_vertices( red.biodom.nw, rm_idx )
    subclust <- igraph::cluster_louvain(tmp, weights = E(tmp)$kappa )
    x$subclust[[i]] <- tibble( id = subclust$names, clust = subclust$membership ) %>% 
      left_join(., biodom %>% select(id = GO_ID, GOterm_Name, n_symbol, symbol), by = 'id') %>% 
      filter(!is.na(GOterm_Name)) %>% 
      group_by(clust) %>% 
      arrange(desc(n_symbol), .by_group = T) %>% 
      ungroup()
    x$n_subclust[i] <- x$subclust[[i]]$clust %>% unique %>% length
  }
  
  biodom.nw.bd.subclusters <- bind_rows(biodom.nw.bd.subclusters, x)
  
}

```


```{r message=FALSE}
bd = biodom.nw.bd.subclusters %>% select(bd, kappa) %>% 
  filter(bd %in% subdom$Biodomain)

olap = tibble()

for(i in 1:nrow(bd)) {
  
  x = bd$bd[i]
  k = bd$kappa[i]
  
  sd = nw.clust %>% filter(biodom ==  x) %>% 
    mutate(clust = str_remove_all(name, '.graphml') ) 
  
  lc = biodom.nw.bd.subclusters %>% filter(bd == x, kappa == k)
  
  if( nrow(lc$subclust[[1]]) == 0 ){ next }
  
  lc = lc %>% pull(subclust) %>% .[[1]] %>% 
    group_by(clust) %>% 
    summarise(symbol = unlist(symbol) %>% unique() %>% list())
  
  olap <- crossing(c = unique(lc$clust), b = unique(sd$clust) ) %>% 
    rowwise() %>% 
    mutate(
      n_c = lc %>% filter( clust == as.numeric(c) ) %>% pull(symbol) %>% unlist() %>% unique() %>% length(),
      n_b = sd %>% filter( clust == b ) %>% pull(nodes) %>% .[[1]] %>% pull(name) %>% unique() %>% length()
    ) %>% 
    group_by(c,b) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             lc %>% filter( clust == as.numeric(c) ) %>% pull(symbol) %>% unlist() %>% unique(),
             sd %>% filter( clust == b ) %>% pull(nodes) %>% .[[1]] %>% pull(name)
             ))
           ) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(.keep = 'all', 
           pct_c = intersect / n_c,
           pct_b = intersect / n_b ) %>%
    ungroup() %>% 
    mutate(
      c = fct_reorder( as.factor(c), n_c),
      b = fct_reorder( as.factor(b), n_b),
      biodom = x,
      kappa = k
    ) %>% 
    bind_rows(olap, .)
  
}

```

```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=5, fig.height=12}

bd = biodom.nw.bd.subclusters %>% select(bd) %>% 
  distinct()

for(i in 1:nrow(bd)) {

  cat("  \n####",  bd$bd[i], "  \n")

  tmp <- olap %>% filter(biodom == bd$bd[i]) 
  
  if(nrow(tmp) == 0){next}
  
  p = ggplot(tmp, aes(y = c, x = b)) +
        geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
        viridis::scale_fill_viridis("% Subdomain", option = "C", direction = -1)+
        geom_text(aes(label = intersect ), size = 2.5) +
        facet_wrap(~kappa, scales = 'free', ncol =1)+
        labs(y='Annotation NW Clusters',x='Path Commons NW Clusters',
             title = bd$bd[i],
             subtitle = 'Genes in Pathway Commons NW clusters vs\nannotation network clusters, filtered by edge kappa')
      
  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
  
}

```

## term enrichment by clustered nodes {.tabset}
```{r}
univ <-as.data.frame(org.Hs.eg.db::org.Hs.egGO) %>%
  pull(gene_id) %>%
  unique() %>%
  gprofiler2::gconvert(., organism = 'hsapiens', target = 'HGNC', numeric_ns = 'ENTREZGENE_ACC') %>% 
  as_tibble() %>% 
  pull('name') %>%
  intersect(., names(V(base.net)) )

nw.clust <- nw.clust %>%
  rename(bd = biodom) %>% 
  rowwise() %>%
  mutate(
    gl = nodes %>% .[[2]] %>% list(),
    enr = gprofiler2::gost( query = unlist(gl),
                            organism = 'hsapiens',
                            domain_scope = 'custom',
                            custom_bg = univ,
                            sources = 'GO',
                            significant = FALSE
                            ) %>%
      .$result %>%
      list()) 

nw.clust <- nw.clust %>%
  rowwise() %>% 
  mutate(
    enr = anno.enr(enr,
                   GO_ID_column = 'term_id',
                   biodomain_table = biodom,
                   domain_colors = biodom %>%
                     select(domain = Biodomain, abbr:color) %>%
                     distinct()
                   ) %>%
      list()
  )

```

```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=6, fig.height=16}

bd <- nw.clust$bd %>% unique %>% sort 

# olap = tibble()
thresh = 1e-2

for(i in 1:length(bd)) {
  
  cat("  \n###",  bd[i], "  \n")
  
  # subset to biodomain
  tmp <- nw.clust %>% 
    rename(biodom = bd) %>% 
    rowwise() %>% 
    mutate(
      name = name %>% str_remove_all('.graphml'),
      name = paste0(name, ', ', length(unlist(unique(nodes))), ' nodes')
    ) %>% 
    filter(biodom == bd[i]) %>% 
    unnest(enr) 
  
  # tally biodom term enrichments
  bdt <- bd.tally(tmp %>% filter(p_value <= thresh) %>% pull(term_name), biodom)
  tmp = tmp %>%
    mutate(
      Biodomain = factor(Biodomain,
                         levels = bdt$domain %>% 
                           str_subset('none', negate = T) %>%
                           c('none',.))
      )
  
  # biodom plot
  p1 = tmp %>%
    ggplot(aes(-log10(p_value), Biodomain))+
    geom_violin(data = subset(tmp, p_value <= thresh), aes(color = color), scale = 'width')+
    geom_jitter(data = subset(tmp, p_value <= thresh), aes(color = color), alpha = .7)+
    scale_color_identity()+
    # xlim(c(0,30))+
    labs(y = '', 
         title = paste0(bd[i], ' cluster enriched terms'), 
         subtitle = paste0('enrichment threshold: ', thresh))+
    facet_wrap(~name, ncol = 3) # , scales = 'free_x'
  
  # compute term overlap
  olap <- crossing( c = unique(tmp$name), b = unique(tmp$name) ) %>% 
    rowwise() %>% 
    mutate(
      n_c = tmp %>% filter(name == c, p_value <= thresh) %>% 
        pull(GO_ID) %>% unique %>% length ,
      n_b = tmp %>% filter(name == b, p_value <= thresh) %>% 
        pull(GO_ID) %>% unique %>% length 
    ) %>% 
    group_by(c,b) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             tmp %>% filter(name == c, p_value <= thresh) %>% pull(GO_ID),
             tmp %>% filter(name == b, p_value <= thresh) %>% pull(GO_ID)
             ))
           ) %>% 
    ungroup() %>% 
    rowwise() %>% 
    mutate(.keep = 'all', 
           pct_c = intersect / n_c,
           pct_b = intersect / n_b ) %>%
    ungroup() %>% 
    mutate(
      c = str_remove_all(c, '.graphml'),
      c = fct_reorder( as.factor(c), n_c),
      b = str_remove_all(b, '.graphml'),
      b = fct_reorder( as.factor(b), n_b)
    ) 
  
  # plot heatmap of term overlap
  p2 = ggplot(olap, aes(x = c, y = b)) +
    geom_tile(aes(fill=pct_b), alpha = .8) + theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    viridis::scale_fill_viridis("% Terms Shared", option = "C", direction = -1)+
    geom_text(aes(label = intersect ), size = 2.5) +
    scale_x_discrete(limits = rev)+
    labs(x='',y='',
         title = paste0(bd[i], ': enriched GO terms overlap across clusters'),
         subtitle = paste0('enrichment threshold: ', thresh)
         )
  
  p = cowplot::plot_grid(p2, p1, ncol = 1, rel_heights = c(.5,1))
  
  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
  
  }

```


# Session
```{r}
sessionInfo()
```

