---
title: "Biodomain-by-Celltype NW"
author: "Greg Cary"
date: "`r Sys.Date()`"
output: 
  html_document: 
    fig_width: 5
    fig_height: 4
  html_notebook:
    code_folding: hide
    theme: readable
    css: style.css
    toc: true
    toc_float: true
---
# Setup

## packages  
```{r setup}
# # Package names
# packages <- c(
#   # 'paxtoolsr','org.Hs.eg.db','HotNetvieweR','clusterProfiler', 
#   'synapser','igraph','tidygraph','ggraph','tidyverse'
#   )
# 
# # Load packages
# invisible(lapply(packages, library, character.only = TRUE))

library(synapser)
library(igraph)
library(tidygraph)
library(ggraph)
library(tidyverse)

source('../../treatAD_biodomains/scripts/biodom_tally.R')
source('../../treatAD_biodomains/scripts/annotate_enr_term_biodomains.R')
source('../../treatAD_biodomains/scripts/biodom_enr_plots.R')

theme_set(theme_bw())
```

## TREAT-AD data
Grab relevant data from synapse, including:
1) Target Risk Scores ([syn25575156](https://www.synapse.org/#!Synapse:syn25575156){target="_blank"}) and Omics Scores ([syn22758536](https://www.synapse.org/#!Synapse:syn22758536){target="_blank"})  
2) Biodomain Definitions ([syn25428992](https://www.synapse.org/#!Synapse:syn25428992){target="_blank"})  
2) Risk-enriched Biodomain Terms ([syn45824995](https://www.synapse.org/#!Synapse:syn45824995){target="_blank"})
3) Base Network ([syn51110930](https://www.synapse.org/#!Synapse:syn51110930){target="_blank"})  
4) Synapse IDs of path-traced NW objects  
5) Synapse IDs of wKDA results 
6) CRISPRbrain simple phenotype screen data  

```{r}
synLogin()

# target risk scores
scores <- read_csv(
  synTableQuery('select * from syn25575156', includeRowIdAndRowVersion = F)$filepath
  , col_types = cols())
omics <- read_csv(
  synTableQuery('select * from syn22758536', includeRowIdAndRowVersion = F)$filepath
  , col_types = cols())

# biological domain annotations
biodom <- full_join(
  # biodomains
  readRDS(synGet('syn25428992')$path),
  # domain labels
  read_csv(synGet('syn26856828')$path, col_types = cols()),
  by = c('Biodomain'='domain')
) %>%
  mutate(Biodomain = case_when(Biodomain == 'none' ~ NA_character_, T ~ Biodomain))

domains = biodom %>% pull(Biodomain) %>% unique() %>% sort()

# enriched biodomain terms
enr.bd <- read_csv( synGet('syn45824995')$path, col_types = cols() ) %>% 
  mutate(leadingEdge_genes = str_split(leadingEdge_genes, '\\|'))

# base network
base_net <- igraph::read_graph(synGet('syn51110930')$path, format = 'graphml') 

# specify directed edge types
directed_edge_types = c("catalysis-precedes",
                        "controls-expression-of",
                        "controls-phosphorylation-of",
                        "controls-state-change-of",
                        "controls-transport-of"
                        )
```

pre-filtered NWs    
```{r}
undir <- base_net

# filt node & edge
tmp <- igraph::delete_vertices(
  base_net,
  igraph::V(base_net)[ igraph::V(base_net)$brain_exp == 0 ]
)
undir_node_edge <- igraph::subgraph.edges(
  tmp,
  igraph::E(tmp)[ igraph::E(tmp)$n_edge_evidence > 1 ],
  delete.vertices = T 
)

# filt node
undir_node <- igraph::delete_vertices(
    base_net,
    igraph::V(base_net)[ igraph::V(base_net)$brain_exp == 0 ]
  )

# filt edge
undir_edge <- igraph::subgraph.edges(
    base_net,
    igraph::E(base_net)[ igraph::E(base_net)$n_edge_evidence > 1 ],
    delete.vertices = T 
  )

# dir
dir <- igraph::subgraph.edges( 
    base_net, 
    igraph::E(base_net)[ igraph::E(base_net)$directed == 1 ],
    delete.vertices = T 
  ) %>% 
    as.directed(mode = 'arbitrary')

# dir node edge
dir_node_edge <- igraph::subgraph.edges( 
    undir_node_edge, 
    igraph::E(undir_node_edge)[ igraph::E(undir_node_edge)$directed == 1 ],
    delete.vertices = T 
  ) %>% 
    as.directed(mode = 'arbitrary')

# dir node
dir_node <- igraph::subgraph.edges( 
    undir_node, 
    igraph::E(undir_node)[ igraph::E(undir_node)$directed == 1 ],
    delete.vertices = T 
  ) %>% 
    as.directed(mode = 'arbitrary')

# dir edge
dir_edge <- igraph::subgraph.edges( 
    undir_edge, 
    igraph::E(undir_edge)[ igraph::E(undir_edge)$directed == 1 ],
    delete.vertices = T 
  ) %>% 
    as.directed(mode = 'arbitrary')

```

## NW & KDA data
<!-- ```{r} -->

<!-- # read NW results dir on Synapse -->
<!-- nw.dirs <- map_dfr( -->
<!--   synGetChildren('syn51739831')$asList() %>% -->
<!--     tibble(f = .) %>% unnest_wider(f) %>% -->
<!--     filter( -->
<!--       !(name %in% c('pseudotime','nanostring_induced_subgraph.graphml', 'key_drivers_all_nw.csv')) -->
<!--       ) %>% -->
<!--     pull(id), -->
<!--   ~{ synGetChildren(  parent = .x  )$asList() %>% -->
<!--       tibble(f = .) %>% unnest_wider(f) %>% -->
<!--       filter(grepl('graphml', name)) %>% -->
<!--       mutate( -->
<!--         bd = str_extract(name, '^(?<=[bdFiltered_]{0,1}).+(?=_[un]*directed)') %>% -->
<!--           str_remove_all('bdFiltered_') %>% str_replace_all('_',' '), -->
<!--         bd.filt = if_else(grepl('bdFiltered',name),T,F), -->
<!--         filt = str_extract(name, '(?<=_filt_).+(?=\\.graphml)'), -->
<!--         dir = str_extract(name, '[un]*directed') -->
<!--         ) %>% -->
<!--       relocate(bd, bd.filt, filt, dir) -->
<!--     } -->
<!-- ) %>% -->
<!--   filter(!grepl('Astro|Micro', filt)) -->

<!-- # read KDA results dir on Synapse -->
<!-- kda.dirs <- map_dfr( -->
<!--   synGetChildren('syn51739831')$asList() %>% -->
<!--     tibble(f = .) %>% unnest_wider(f) %>% -->
<!--     filter( -->
<!--       !(name %in% c('pseudotime','nanostring_induced_subgraph.graphml', 'key_drivers_all_nw.csv')) -->
<!--       ) %>% -->
<!--     pull(id), -->
<!--   ~{ id = synGetChildren( parent = .x )$asList() %>% -->
<!--       tibble(f = .) %>% unnest_wider(f) %>% -->
<!--       filter(grepl('kda', name)) %>% pull(id) -->

<!--      bd = synGet(.x)$properties$name -->

<!--      synGetChildren(id)$asList() %>% -->
<!--        tibble(f = .) %>% unnest_wider(f) %>% -->
<!--        filter(grepl('results|tophits',name)) %>% -->
<!--        mutate( -->
<!--           bd = bd %>% str_replace_all('_' ,' '), -->
<!--           filt = str_extract(name, '(?<=_filt_).+(?=_addWeights)'), -->
<!--           dir = str_extract(name, '[un]*directed'), -->
<!--           ef = str_extract(name, '(?<=_edgeFactor_)[0|1]') -->
<!--           ) %>% -->
<!--         relocate(bd, filt, dir, ef) -->
<!--     } -->
<!-- ) %>% -->
<!--   mutate(set = case_when(grepl('results', name) ~ 'full', grepl('top',name) ~ 'top', T ~ NA_character_)) %>% -->
<!--   relocate(set) %>% -->
<!--   filter(!grepl('Astro|Micro', filt)) -->
<!-- ``` -->

read local results directories
```{r}
# # read local results dir
# doms = list.files('../results/biodomain')
# nw.dirs <- tibble(bd = doms, i = 1:length(doms)) %>% 
#   rowwise() %>% 
#   mutate(
#     f = list.files( paste0('../results/biodomain/',bd) ) %>% list(),
#     kd = list.files( paste0('../results/biodomain/',bd,'/kda') ) %>% list()
#   )
# nw.dirs$kd[[ match('APP_Metabolism', nw.dirs$bd) ]]

# i = which(doms == 'Immune_Response')

# # check which trace / KDA jobs have completed
# nw.dirs %>% rowwise() %>% mutate(n = length(unlist(kd))) %>% arrange(desc(n))
```

## functions

<!-- read nw data (synapse)   -->
<!-- ```{r} -->
<!-- read_nw <- function(dom_idx){ -->

<!--   nw = read.graph( -->
<!--     synGet( -->
<!--       doms$nw.dir[[dom_idx]] %>% filter( grepl('bdFiltered.+graphml', name) ) %>% pull(id) -->
<!--     )$path, -->
<!--     format = 'graphml' -->
<!--     ) -->

<!--   return(nw) -->

<!-- } -->

<!-- # read_nw <- function(dom_idx){ -->
<!-- #   nw = read.graph( -->
<!-- #     paste0(here::here(), '/results/biodomain/', doms[dom_idx], '/', -->
<!-- #            nw.dirs$f[[match(doms[dom_idx], nw.dirs$bd)]] %>% -->
<!-- #              str_subset(., 'bdFiltered') %>% str_subset('graphml')), -->
<!-- #     format = 'graphml') -->
<!-- #  -->
<!-- #   return(nw) -->
<!-- # } -->
<!-- ``` -->

read synapse directories into a tibble
```{r}
read_syn_dir <- function(parent_id){
  synapser::synGetChildren(parent_id)$asList() %>%
    tibble(f = .) %>% unnest_wider(f)
}
```

 
NW info 
```{r}
v_info <- function(net){
  v.attr <- tibble( na = vertex.attributes(net) ) %>% t() %>% 
    as_tibble(rownames = NA, .name_repair = ~vertex_attr_names(net) ) %>% 
    unnest(everything()) 
}

e_info <- function(net){
  e.attr <- tibble( ea = edge.attributes(net) ) %>% t() %>% 
    as_tibble(rownames = NA, .name_repair = ~edge_attr_names(net) ) %>% 
    unnest(everything()) 
}
```

read KDA result data  
```{r}
# remote from synase
read_kd_remote <- function(kda_dir_syn_id){
  
  synDir <- synGetChildren(kda_dir_syn_id)$asList() %>%
  tibble(f = .) %>% unnest_wider(f)
  
  
  kd.ef0 <- read_tsv(
    synGet( 
      synDir %>% filter( grepl('edgeFactor_0.results.txt', name) ) %>% pull(id)
      )$path, 
    col_types = cols())
  kd.ef1 <- read_tsv(
    synGet( 
      synDir %>% filter( grepl('edgeFactor_1.results.txt', name) ) %>% pull(id)
      )$path, 
    col_types = cols())
  kd.top <- read_tsv(
    synGet( 
      synDir %>% filter( grepl('edgeFactor_1.tophits.txt', name) ) %>% pull(id)
      )$path, 
    col_types = cols()) %>% 
    mutate(kd = paste0(NODE,'-',MODULE))
    
  kd = bind_rows(
    kd.ef0 %>% mutate(ef = 'ef0_fdr'),
    kd.ef1 %>% mutate(ef = 'ef1_fdr')
    ) %>% 
    mutate(FDR = -log10(FDR)) %>%
    pivot_wider(id_cols = c(MODULE, NODE, MEMBER), 
                names_from = ef, values_from = FDR, values_fill = 0) %>%
    mutate(delta_fdr = ef1_fdr - ef0_fdr) %>% arrange(desc(delta_fdr)) %>% 
    mutate(top = 0)
  
  if( any( kd.top$FDR < 0.05 ) ){
    kd$top[ which(paste0(kd$NODE,'-',kd$MODULE) %in% kd.top$kd[kd.top$FDR < 0.05]) ] <- 1
  }
  
  return(kd)
}

# local directory
read_kd_local <- function(local_path){
  
  kd.pth <- list.files(local_path, full.names = T)
  
  kd.ef0 <- read_tsv(
    kd.pth %>% str_subset('edgeFactor_0.results.txt'), 
    col_types = cols())
  kd.ef1 <- read_tsv(
    kd.pth %>% str_subset('edgeFactor_1.results.txt'),  
    col_types = cols())
  kd.top <- read_tsv(
    kd.pth %>% str_subset('edgeFactor_1.tophits.txt'), 
    col_types = cols()) %>% 
    mutate(kd = paste0(NODE,'-',MODULE))
    
  kd = bind_rows(
    kd.ef0 %>% mutate(ef = 'ef0_fdr'),
    kd.ef1 %>% mutate(ef = 'ef1_fdr')
    ) %>% 
    mutate(FDR = -log10(FDR)) %>%
    pivot_wider(id_cols = c(MODULE, NODE, MEMBER), 
                names_from = ef, values_from = FDR, values_fill = 0) %>%
    mutate(delta_fdr = ef1_fdr - ef0_fdr) %>% arrange(desc(delta_fdr)) %>% 
    mutate(top = 0)
  
  if( any( kd.top$FDR < 0.05 ) ){
    kd$top[ which(paste0(kd$NODE,'-',kd$MODULE) %in% kd.top$kd[kd.top$FDR < 0.05]) ] <- 1
  }
  
  return(kd)
}

```

plot subnetwork around identified KDs  
```{r}
plot_kd_subnet <- function(nw, kd, term) {
  
  vert_num <- match(kd, V(nw)$name)
  
  vert_neigh <- neighbors(nw, vert_num)
  
  term_num <- biodom %>%
    filter(GOterm_Name == term) %>%
    pull(symbol) %>% unlist() %>%
    match(., V(nw)$name) %>% .[!is.na(.)]
  
  g2 <- induced_subgraph(nw, c(vert_num, intersect(term_num, vert_neigh)))
  g3 <- induced_subgraph(nw, c(vert_num, term_num))
  
  cowplot::plot_grid(
    
    ggraph(g3, layout = 'linear', circular = TRUE) +
      geom_edge_arc(alpha = .3, color = 'grey75') +
      geom_node_point( shape = 21, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter= .N()$name != kd)  )+
      geom_node_point( shape = 23, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter = .N()$name == kd) )+
      geom_node_text(aes(label = name), size = 2) +
      coord_fixed() +
      scale_size_continuous( range = c(.5, 10), limits = c(0, 5), trans = 'exp')+
      scale_fill_gradient2(
        low = 'purple', mid = 'grey20', high = 'green', na.value = 'grey85',
        limits = c(-2.5,2.5) )+ #approx: range(omics$Pro_TE, na.rm = T)
      labs( title = 'All term genes in NW',
            subtitle = paste0('KD: ', kd, '\nTerm: ', term) )+
      theme_graph(background = 'white')
    ,
    ggraph(g2, layout = 'linear', circular = TRUE) +
            geom_edge_arc(alpha = .3, color = 'grey75') +
      geom_node_point( shape = 21, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter= .N()$name != kd)  )+
      geom_node_point( shape = 23, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter = .N()$name == kd) )+
      geom_node_text(aes(label = name), size = 2) +
      coord_fixed() +
      scale_size_continuous( range = c(.5, 10), limits = c(0, 5), trans = 'exp')+
      scale_fill_gradient2(
        low = 'purple', mid = 'grey20', high = 'green', na.value = 'grey85',
        limits = c(-2.5,2.5) )+ #approx: range(omics$Pro_TE, na.rm = T)
      labs( title = 'Term genes & KD neighbors in NW',
            subtitle = paste0('KD: ', kd, '\nTerm: ', term) )+
      theme_graph(background = 'white')
    ,
    ncol = 2
    
  )
}
```

# Biodom-by-celltype NW analysis

```{r}
syn.dir <- read_syn_dir('syn52383741') # biodomain by cell type

doms  <-  map_dfr(1:nrow(syn.dir), 
                  ~ read_syn_dir(syn.dir$id[.x]) %>% 
                    mutate(parent = syn.dir$name[.x]) %>% 
                    relocate(parent)) %>%
  rowwise() %>% 
  mutate(nw.dir = read_syn_dir(id) %>% list(),
         kd.dir = read_syn_dir(id) %>% filter(name == 'kda') %>% pull(id) %>% 
           read_syn_dir(.) %>% list(), 
         celltype = str_split_fixed(parent, '_', 2)[,2] %>% str_to_sentence()) %>% 
  select(celltype, bd = name, id, nw.dir, kd.dir)
```

## cell type gene sets

```{r}
ct_nodes = v_info(undir_node_edge) %>% 
  select(gene = name, Exc, Inh, Astro, Micro) %>% 
  pivot_longer(cols = Exc:Micro) %>% 
  filter(value == 1) %>% 
  group_by(name) %>% 
  summarise( n = length(unique(gene)),
             gene = list(unique(gene)) ) %>% 
  mutate(name = fct_reorder(name, n)) %>% 
  arrange(desc(n))
```

```{r}
olap <- crossing(nw1 = ct_nodes$name, nw2 = ct_nodes$name) %>% 
  group_by(nw1,nw2) %>% 
  mutate(.keep = 'all', 
         intersect = length(intersect(
           ct_nodes %>% filter(name == nw1) %>% pull(gene) %>% unlist(),
           ct_nodes %>% filter(name == nw2) %>% pull(gene) %>% unlist()
           ))
         ) %>% 
  ungroup() %>% group_by(nw1) %>% 
  mutate(.keep = 'all', 
         pct_overlap = 100*(intersect / intersect[which(nw2 == nw1)]) ) %>% 
  ungroup() %>%
  mutate(
    nw1 = fct_relevel(nw1, ct_nodes$name[order(ct_nodes$n)] %>% as.character),
    nw2 = fct_relevel(nw2, ct_nodes$name[order(ct_nodes$n, decreasing = T)] %>% as.character)
    ) 
```


```{r fig.width=8, fig.height=4}

plot_row <- cowplot::plot_grid(
  ggplot(ct_nodes, aes(n, name)) +
    geom_bar(stat = 'identity', color = 'grey30', width = .7)+
    theme( axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1) )+
    # scale_x_log10()+
    labs(y = '',x = '# nodes')  
  ,
  ggplot(olap, aes(x = nw2, y = nw1)) +
    geom_tile(aes(fill=pct_overlap), alpha = .8) + theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    viridis::scale_fill_viridis("% Total", option = "A", direction = -1)+
    geom_text(aes(label = intersect ), color = 'grey66', size = 3) +
    labs(x='',y='') 
  , nrow = 1, rel_widths = c(.6,1)
)

title <- cowplot::plot_grid(
  cowplot::ggdraw() + 
  cowplot::draw_label( 'Cell Type Genes', fontface = 'bold', x = 0, hjust = 0 )
  ,
  cowplot::ggdraw() + 
  cowplot::draw_label( 'genes annotated to each cell type in filtered base NW',
                       x = 0, hjust = 0 )
  , ncol = 1
  ) +
  theme( plot.margin = margin(0, 0, 0, 7) )

cowplot::plot_grid(
  title, plot_row, ncol = 1,
  rel_heights = c(0.15, 1)
)


```


## Calculate NW stats

```{r}
nw.dat = doms %>% 
  select(celltype, bd, id) 

# future::plan('multisession')
x = furrr::future_map_dfr(
  1:nrow(nw.dat),
  ~{synLogin()
    nw = doms$nw.dir[[.x]] %>% 
      filter( grepl('bdFiltered.+graphml', name) ) %>% 
      pull(id) %>% synGet(.) %>% .$path %>% 
      read_graph(., format = 'graphml')
    snw = igraph::simplify(nw, remove.multiple = T)
    tibble(
      avg_node_degree = degree(snw, V(snw)) %>% mean(),
      avg_path_length = snw %>% average.path.length,
      assortativity_coef = snw %>% assortativity(., types1 = V(.)),
      connected_components = snw %>% no.clusters,
      edges = E(nw)$edge %>% unique() %>% list(),
      nodes = V(nw) %>% names() %>% unique() %>% list()
    )
  }
)
# future::plan('sequential')

nw.dat = bind_cols(nw.dat, x)

nw.dat$q_genes <- map(
  1:nrow(nw.dat),
  ~ doms$nw.dir[[.x]] %>% filter( grepl('queryList', name) ) %>% 
    pull(id) %>% synGet(.) %>% .$path %>% 
    read_tsv(., col_names = F, col_types = cols()) %>% 
    pull(X1) 
)

nw.dat$input_genes <- map(
  1:nrow(nw.dat),
  ~ intersect( unlist(nw.dat$q_genes[.x]), 
               names(V(undir_node_edge)[which(vertex_attr(undir_node_edge, nw.dat$celltype[.x])==1)])  )
)

nw.dat$added_genes <- map(
  1:nrow(nw.dat),
  ~ setdiff( nw.dat$nodes[[.x]], nw.dat$input_genes[[.x]] ) 
)

# -common nodes
# V(nw) %>% names() %>% unique() %>% length()
# -common edges
# E(nw)$edge %>% head()
#  by filt, direction
```

## NW size
```{r}
nw.summary <- nw.dat %>% 
  group_by(bd, celltype) %>% 
  summarise(
    input = length(unique(unlist(input_genes))),
    added = length(unique(unlist(added_genes))),
    n_nodes = length(unique(unlist(nodes))),
    n_edges = length(unique(unlist(edges)))
  ) %>% 
  mutate(
    n_possible_edge = (n_nodes * (n_nodes-1))/2,
    fxn_possible = n_edges/n_possible_edge
  )

# to calculate the number of possible edges in a graph with N nodes
# directed graph: N*(N-1)
# undriected graph: (N * (N-1)) / 2
nw.summary$n_possible_edge = map_dbl(1:nrow(nw.summary), ~ ( nw.summary$n_nodes[.x] * (nw.summary$n_nodes[.x]-1)) / 2)
nw.summary$fxn_possible = map_dbl(1:nrow(nw.summary), ~ nw.summary$n_edges[.x] / nw.summary$n_possible_edge[.x] )
```

```{r warning=FALSE, fig.width=12, fig.height=6}
nw.summary %>% 
  mutate(bd = str_replace_all(bd, '_' ,' ')) %>% 
  left_join(., biodom %>% select(bd = Biodomain, color, abbr ) %>% distinct() ) %>% 
  # filter(dir == 'undirected', filt == 'node_edge') %>% 
  pivot_longer(cols = c(n_nodes, n_edges
                        # , fxn_possible
                        )) %>% 
  mutate( 
    max = case_when(
      name == 'n_nodes' ~ V(undir_node_edge) %>% length(),
      name == 'n_edges' ~ E(undir_node_edge) %>% length(),
      name == 'fxn_possible' ~ integer(1)),
    name = fct_relevel(name, c('n_nodes','n_edges', 'fxn_possible'))
    ) %>% 
  ggplot(aes(input, value))+
  geom_smooth(method = 'lm', color = 'grey60', fill = 'grey85', 
              lwd = .5, lty = 2)+
  geom_point(aes(fill = color, shape = celltype), size = 3, alpha = .5)+
  ggrepel::geom_text_repel(aes(label = paste0(abbr,'-',celltype)), size = 2.5)+
  geom_hline(aes(yintercept = max), lty = 2)+
  scale_y_log10()+
  scale_x_log10()+
  scale_fill_identity()+
  scale_shape_manual(values = 21:24)+
  labs(x = '# input genes\n(query set overlap with filtered base NW)', 
       y = '# NW features')+
  facet_wrap(~name, scales = 'free')
```

```{r warning=FALSE, fig.width=6, fig.height=5}
nw.summary %>% 
  mutate(bd = str_replace_all(bd, '_' ,' ')) %>% 
  left_join(., biodom %>% select(bd = Biodomain, color, abbr ) %>% distinct() ) %>% 
  mutate( max = V(undir_node_edge) %>% length() ) %>% 
  ggplot(aes(input, added))+
  geom_smooth(method = 'lm', color = 'grey60', fill = 'grey85', 
              lwd = .5, lty = 2)+
  geom_point(aes(fill = color, shape = celltype), 
             size = 3, alpha = .5)+
  ggrepel::geom_text_repel(aes(label = abbr), size = 2.5)+
  geom_hline(aes(yintercept = max), lty = 2)+
  scale_y_log10()+ scale_x_log10()+
  scale_shape_manual(values = 21:24)+
  scale_fill_identity()+
  labs(x = '# input nodes\n(query set overlap with filtered base NW)', 
       y = '# nodes added by pathway reconstruction')
```

## NW properties ~ Biodomains
Global properties of biodomain-filtered path traced networks
```{r fig.width=12, fig.height=7}
nodes = v_info(undir_node_edge) %>% 
  select(gene = name, Exc, Inh, Astro, Micro) %>% 
  pivot_longer(cols = Exc:Micro) %>% 
  filter(value == 1) %>% 
  group_by(name) %>% 
  summarise(n = length(unique(gene))) %>% 
  arrange(desc(n)) %>% 
  mutate(bd = 'Base NW', properties = 'input', color = 'black',
         name = fct_reorder(name, n)) %>%
  rename(val = n, celltype = name)

tmp <- nw.dat %>% 
  mutate(bd = str_replace_all(bd, '_' ,' ')) %>% 
  left_join(., biodom %>% select(bd = Biodomain, color, abbr ) %>% distinct(), by = 'bd' ) %>% 
  select( celltype, bd, input = input_genes, added = added_genes, color:abbr ) %>%
  rowwise() %>%
  mutate( across( input:added, ~ length(unique(unlist(.x))) ) ) %>% 
  pivot_longer(cols = c(added, input), names_to = 'properties', values_to = 'val') %>% 
  mutate(
    properties = factor(properties, levels = c('added', 'input')),
    celltype = factor( celltype, nodes$celltype )
         ) %>% 
  mutate(bd = str_replace_all(bd, ' ','\n')) 

tmp <- bind_rows(nodes,tmp) %>% 
  mutate(bd = factor(bd, levels = unique(bd) %>% 
                       str_subset(., 'base NW', negate = T) %>% 
                       c(.,'base NW')))

ggplot(tmp, aes(val, celltype, group = properties)) +
  geom_bar(stat = 'identity', 
           aes(fill = color, alpha = properties), #scales = 'free_x',alpha = .8, 
           color = 'grey30', width = .7)+
  theme(legend.position = 'top', 
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  labs(y = '',x = '# nodes')+
  scale_fill_identity()+
  scale_alpha_discrete('',range = c(.8,.3), limits = rev)+
  # scale_x_log10()+
  facet_wrap(~bd,scales = 'free_x', ncol = 9) #

```

## Overlapping NW elements
```{r warning=FALSE}
nw.dat$bdct = paste0(nw.dat$bd,' - ',nw.dat$celltype)

bd.ord = nw.dat %>% select(bd, bdct, input_genes) %>% distinct() %>% 
    mutate(len = length(unlist(input_genes))) %>% 
    arrange(desc(len), .by_group = T) %>% 
    pull(bd) %>% unique()

bdct.ord <- nw.dat %>% select(bd, bdct, input_genes) %>% distinct() %>% 
    mutate(len = length(unlist(input_genes))) %>% 
    arrange(desc(len), .by_group = T) %>% 
    mutate(bd = fct_relevel(bd, bd.ord)) %>% 
    arrange(bd) %>% 
    pull(bdct)
```

### Inputs
Query genes
```{r fig.width=14, fig.height=12}
olap <- crossing(nw1 = nw.dat$bdct, nw2 = nw.dat$bdct) %>% 
  group_by(nw1,nw2) %>% 
  mutate(.keep = 'all', 
         intersect = length(intersect(
           nw.dat %>% filter(bdct == nw1) %>% pull(input_genes) %>% unlist(),
           nw.dat %>% filter(bdct == nw2) %>% pull(input_genes) %>% unlist()
           ))
         ) %>% 
  ungroup() %>% group_by(nw1) %>% 
  mutate(.keep = 'all', pct_overlap = 100*(intersect / intersect[which(nw2 == nw1)]) ) %>% 
  ungroup() %>%
  mutate(
    nw1 = fct_relevel(nw1, rev(bdct.ord)),
    nw2 = fct_relevel(nw2, bdct.ord)
    ) 

ggplot(olap, aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap), alpha = .8) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  viridis::scale_fill_viridis("% Total", option = "A", direction = -1)+
  geom_text(aes(label = intersect ), color = 'grey66', size = 2) +
  labs(x='',y='', title = 'Input Genes', 
       subtitle = 'query genes overlap with filtered base NW nodes') 
```

### Nodes

```{r fig.width=14, fig.height=12}
olap <- crossing(nw1 = nw.dat$bdct, nw2 = nw.dat$bdct) %>% 
    group_by(nw1,nw2) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             nw.dat %>% filter(bdct == nw1) %>% pull(nodes) %>% unlist(),
             nw.dat %>% filter(bdct == nw2) %>% pull(nodes) %>% unlist()
             ))
           ) %>% 
    ungroup() %>% group_by(nw1) %>% 
    mutate(.keep = 'all', pct_overlap = 100*(intersect / intersect[which(nw2 == nw1)])) %>% 
    ungroup()

olap <- olap %>% 
    mutate(
      nw1 = fct_relevel(nw1, rev(bdct.ord)),
      nw2 = fct_relevel(nw2, bdct.ord)
    ) 

olap %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap), alpha = .8) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  viridis::scale_fill_viridis("% Total", option = "A", direction = -1)+
  geom_text(aes(label = intersect ), color = 'grey66', size = 2) +
  labs(x='',y='', title = 'common nodes') 

```

### Added Nodes
```{r fig.width=14, fig.height=12}
olap <- crossing(nw1 = nw.dat$bdct, nw2 = nw.dat$bdct) %>% 
    group_by(nw1,nw2) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             nw.dat %>% filter(bdct == nw1) %>% pull(added_genes) %>% unlist(),
             nw.dat %>% filter(bdct == nw2) %>% pull(added_genes) %>% unlist()
             ))
           ) %>% 
    ungroup() %>% group_by(nw1) %>% 
    mutate(.keep = 'all', pct_overlap = 100*(intersect / intersect[which(nw2 == nw1)])) %>% 
    ungroup()

olap <- olap %>% 
    mutate(
      nw1 = fct_relevel(nw1, rev(bdct.ord)),
      nw2 = fct_relevel(nw2, bdct.ord)
    ) 

olap %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap), alpha = .8) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  viridis::scale_fill_viridis("% Total", option = "A", direction = -1)+
  geom_text(aes(label = intersect ), color = 'grey66', size = 2) +
  labs(x='',y='', title = 'Nodes added by shortest path reconstruction') 

```


### Edges
common edges
```{r fig.width=14, fig.height=12}

olap <- crossing(nw1 = nw.dat$bdct, nw2 = nw.dat$bdct) %>% 
    group_by(nw1,nw2) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             nw.dat %>% filter(bdct == nw1) %>% pull(edges) %>% unlist(),
             nw.dat %>% filter(bdct == nw2) %>% pull(edges) %>% unlist()
             ))
           ) %>% 
    ungroup() %>% group_by(nw1) %>% 
    mutate(.keep = 'all', pct_overlap = 100*(intersect / intersect[which(nw2 == nw1)]) ) %>% 
    ungroup()

olap <- olap %>% 
    mutate(
      nw1 = fct_relevel(nw1, rev(bdct.ord)),
      nw2 = fct_relevel(nw2, bdct.ord)
    ) 

olap %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap), alpha = .8) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  viridis::scale_fill_viridis("% Total", option = "A", direction = -1)+
  geom_text(aes(label = intersect ), color = 'grey66', size = 1.5) +
  labs(x='',y='', title = 'common edges') 

```

### input, added, total nodes in common

```{r}
olap <- crossing(nw1 = nw.dat$bdct, nw2 = nw.dat$bdct) %>% 
  group_by(nw1,nw2) %>% 
  mutate(.keep = 'all', 
         
         input = length(intersect(
           nw.dat %>% filter(bdct == nw1) %>% pull(input_genes) %>% unlist(),
           nw.dat %>% filter(bdct == nw2) %>% pull(input_genes) %>% unlist()
           )),
         
         added = length(intersect(
           nw.dat %>% filter(bdct == nw1) %>% pull(added_genes) %>% unlist(),
           nw.dat %>% filter(bdct == nw2) %>% pull(added_genes) %>% unlist()
             )),
         
         total = length(intersect(
             nw.dat %>% filter(bdct == nw1) %>% pull(nodes) %>% unlist(),
             nw.dat %>% filter(bdct == nw2) %>% pull(nodes) %>% unlist()
             )),
         
         len_nw1 = nw.dat %>% filter(bdct == nw1) %>% pull(nodes) %>% 
           unlist() %>% unique() %>% length()
         
         ) %>% 
  ungroup() %>% group_by(nw1) %>% 
  mutate(.keep = 'all', 
         input_overlap = input / input[which(nw2 == nw1)],
         added_overlap = added / added[which(nw2 == nw1)],
         total_overlap = total / total[which(nw2 == nw1)],
         ) %>% 
  ungroup() 

olap <- olap %>% 
  pivot_longer(input:total, names_to = 'set', values_to = 'n') %>% 
  mutate(
    set = fct_relevel(set, c('total','input','added')), 
    pct = 100*(n / len_nw1),
    nw1 = fct_relevel(nw1, rev(bdct.ord)),
    nw2 = fct_relevel(nw2, bdct.ord)
    ) 
```

```{r fig.width=24, fig.height=12}

olap %>%
  filter(set != 'total') %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct), alpha = .8) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  viridis::scale_fill_viridis("% Total Nodes", option = "A", direction = -1)+
  geom_text(aes(label = round(pct,2) ), color = 'grey66', size = 2) +
  facet_wrap(~set, nrow = 1)+
  labs(x='',y='') 

```

## Query vs Added gene scores  
```{r}
tmp <- nw.dat %>% 
  select(bd,celltype, bdct, input_genes, added_genes) %>% 
  pivot_longer(cols = c(input_genes, added_genes)) %>% 
  unnest(value) %>% rename(gene = value) %>%  
  left_join(
    .,
    scores %>% select(gene = GeneName, Overall, GeneticsScore, OmicsScore, LiteratureScore),
    by = 'gene', na_matches = 'never'
  ) %>% 
  bind_rows(
    left_join(
      scores %>% select(gene = GeneName, Overall, GeneticsScore, OmicsScore, LiteratureScore), 
      v_info(undir_node_edge) %>% select(gene = name, Exc, Inh, Astro, Micro) %>% 
        pivot_longer(Exc:Micro) %>% filter(value == 1) %>% select(gene, celltype = name) ,
      by = 'gene', na_matches = 'never') %>% 
      mutate(name = 'all_scores') %>% 
      filter(!is.na(gene), !is.na(celltype))
  ) %>% 
  mutate(
    name = factor(name, levels = c('input_genes','added_genes','all_scores'))
  )
```


```{r fig.width=7, fig.height=3}
tmp %>% 
  select(-bd) %>% distinct() %>% 
  rename(set = name) %>% 
  group_by(set) %>% 
  mutate(set = paste0(set, '\n(', length(unique(gene)), ' genes)'),
         set = fct_relevel(set, unique(set)[c(2,3,1)])) %>% 
  ggplot(aes(Overall))+
  theme(legend.position = 'top') + 
  geom_density(aes(fill = set, color = set), alpha = .3)+
  facet_wrap(~celltype, ncol = 4)
  # geom_histogram(aes(fill = set), alpha = .8, position='dodge')
```

```{r fig.width=6, fig.height=5}
tmp %>% 
  select(-bd) %>% distinct() %>% 
  rename(set = name) %>% 
  pivot_longer(Overall:OmicsScore) %>% 
  filter(value >0) %>% 
  ggplot(aes(value))+
  theme(legend.position = 'top') + 
  geom_density(aes(fill = set), color = 'grey70', alpha = .3)+
  # geom_histogram(aes(fill = set),  alpha = .8, position='dodge')+
  labs(x='score')+
  facet_grid(celltype~name, scales = 'free')
```

```{r fig.width=5, fig.height=15}
tmp %>% 
  rename(set = name) %>% 
  filter(set!='all_scores') %>% 
  pivot_longer(Overall:OmicsScore) %>% 
  filter(value > 0) %>% 
  mutate(bd = str_replace_all(bd, '_','\n')) %>% 
  ggplot(aes(value))+
  theme(legend.position = 'top') + 
  # geom_density(aes(fill = set, color = set), alpha = .3)+
  geom_histogram(aes(fill = set), alpha = .8, position='dodge')+
  facet_grid(bd~name, scales = 'free')
```

```{r fig.width=12, fig.height=18}
tmp %>% 
  filter( name != 'all_scores' ) %>% 
  rename(set = name) %>% 
  # mutate(bd = str_replace_all(bd, '_','\n')) %>% 
  ggplot(aes(Overall))+
  theme(legend.position = 'top') + 
  # geom_density(aes(fill = set), color = 'grey70', alpha = .3)+
  geom_histogram(aes(fill = set), alpha = .8, position='dodge')+
  labs(x = 'TREAT-AD Target Risk Score')+
  facet_wrap(bd~celltype, scales = 'free', ncol = 8)
```

## Biodom Enrichment - NW nodes {.tabset}

```{r}
univ <-as.data.frame(org.Hs.eg.db::org.Hs.egGO) %>%
  pull(gene_id) %>%
  unique() %>%
  gprofiler2::gconvert(., organism = 'hsapiens', target = 'HGNC', numeric_ns = 'ENTREZGENE_ACC') %>% 
  as_tibble() %>% 
  pull('name') %>%
  intersect(., names(V(base_net)) )

gl <- nw.dat %>%
  select(bd, celltype, nodes, input_genes, added_genes) %>%
  pivot_longer(nodes:added_genes) %>%
  rowwise() %>%
  mutate(
    enr = gprofiler2::gost( query = unlist(value),
                            organism = 'hsapiens',
                            domain_scope = 'custom',
                            custom_bg = univ,
                            sources = 'GO'
                            ) %>%
      .$result %>%
      list()
  ) 

gl <- gl %>% 
  unnest(enr) %>% 
  anno.enr(., GO_ID_column = 'term_id', biodomain_table = biodom,
           domain_colors = biodom %>% select(domain = Biodomain, abbr:color) %>% distinct()) 

```


```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=6, fig.height=8}
for(dom in unique(gl$bd)){
  
  thresh = 1e-15
  
  tmp <- gl %>% filter( bd == dom, Biodomain != 'none')
  
  bdt <- bd.tally(tmp %>% filter(p_value <= thresh) %>% pull(term_name), biodom)
  
  tmp = tmp %>%
    rowwise() %>%
    mutate(bd = paste0(bd,'\n', length(unique(unlist(value))), ' input genes') ) %>%
    mutate(Biodomain = factor(Biodomain,
                              levels = bdt$domain %>%
                                str_subset('none', negate = T) %>%
                                c('none',.))
           , name = factor(name, levels = c('input_genes','added_genes','nodes'))
           )
  
  p = tmp %>%
    ggplot(aes(-log10(p_value), Biodomain))+
    geom_violin(data = subset(tmp, p_value <= thresh), aes(color = color), scale = 'width')+
    geom_jitter(data = subset(tmp, p_value <= thresh), aes(color = color), alpha = .7)+
    scale_color_identity()+
    # xlim(c(0,30))+
    labs(y = ''
         , title = dom
         , subtitle = paste0('p-value threshold: ', thresh))+
    facet_grid(celltype~name) # , scales = 'free_x'
    
  cat("  \n###",  dom, " graph  \n")
  plot(p)
  plot.new()
  dev.off()
  cat("  \n  \n")  
}
```



# Session
```{r}
sessionInfo()
```

