---
title: "Sub-domain NW Key Drivers"
author: "Greg Cary"
date: "`r Sys.Date()`"
output: 
  html_document: 
    fig_width: 5
    fig_height: 4
  html_notebook:
    code_folding: hide
    theme: readable
    css: style.css
    toc: true
    toc_float: true
---
# Setup

```{r setup}
# # Package names
# packages <- c(
#   # 'paxtoolsr','org.Hs.eg.db','HotNetvieweR','clusterProfiler', 
#   'synapser','igraph','tidygraph','ggraph','tidyverse'
#   )
# 
# # Load packages
# invisible(lapply(packages, library, character.only = TRUE))

library(synapser)
library(igraph)
library(tidygraph)
library(ggraph)
library(tidyverse)

source('../../treatAD_biodomains/scripts/biodom_tally.R')
source('../../treatAD_biodomains/scripts/annotate_enr_term_biodomains.R')
source('../../treatAD_biodomains/scripts/biodom_enr_plots.R')

theme_set(theme_bw())
```

## functions
<!-- nw data   -->
<!-- ```{r} -->
<!-- read_nw <- function(dom_idx){ -->

<!--   nw = read.graph( -->
<!--     synGet( -->
<!--       doms$nw.dir[[dom_idx]] %>% filter( grepl('bdFiltered.+graphml', name) ) %>% pull(id) -->
<!--     )$path, -->
<!--     format = 'graphml' -->
<!--     ) -->

<!--   return(nw) -->

<!-- } -->
<!-- ``` -->

read synapse directories into a dataframe
```{r}
read_syn_dir <- function(parent_id){
  synapser::synGetChildren(parent_id)$asList() %>%
    tibble(f = .) %>% unnest_wider(f)
}
```
 
NW info 
```{r}
v_info <- function(net){
  v.attr <- tibble( na = vertex.attributes(net) ) %>% t() %>% 
    as_tibble(rownames = NA, .name_repair = ~vertex_attr_names(net) ) %>% 
    unnest(everything()) 
}

e_info <- function(net){
  e.attr <- tibble( ea = edge.attributes(net) ) %>% t() %>% 
    as_tibble(rownames = NA, .name_repair = ~edge_attr_names(net) ) %>% 
    unnest(everything()) 
}
```

read KDA result data  
```{r}
read_kd <- function(path){
  
  # detect if KDA dir path is on synapse
  if(substr(path,1,3) == 'syn'){
        
    synDir <- synGetChildren(path)$asList() %>%
      tibble(f = .) %>% unnest_wider(f)
    
    res <- synDir %>% filter(grepl('edgeFactor', name)) %>% pull(name)
    
    if( length(res) < 10 ){ 
      simpleError('Not a full KD results set')
      return(NULL)
      }
    
    kd.ef0 <- read_tsv(
      synGet( 
        synDir %>% filter( grepl('edgeFactor_0.results.txt', name) ) %>% pull(id)
        )$path, 
        col_types = cols())
    ef0.top <- read_tsv(
      synGet( 
        synDir %>% filter( grepl('edgeFactor_0.tophits.txt', name) ) %>% pull(id)
        )$path, 
      col_types = cols()) %>% 
      mutate(kd = paste0(NODE,'-',MODULE))
    
    kd.ef1 <- read_tsv(
      synGet( 
        synDir %>% filter( grepl('edgeFactor_1.results.txt', name) ) %>% pull(id)
        )$path, 
      col_types = cols())
    ef1.top <- read_tsv(
      synGet( 
        synDir %>% filter( grepl('edgeFactor_1.tophits.txt', name) ) %>% pull(id)
        )$path, 
      col_types = cols()) %>% 
      mutate(kd = paste0(NODE,'-',MODULE))
  
  # or read from a local path
  } else {
    
    kd.pth <- list.files(path, full.names = T)
  
    kd.ef0 <- read_tsv(
      kd.pth %>% str_subset('edgeFactor_0.results.txt'), 
      col_types = cols())
    ef0.top <- read_tsv(
      kd.pth %>% str_subset('edgeFactor_0.tophits.txt'), 
      col_types = cols()) %>% 
      mutate(kd = paste0(NODE,'-',MODULE))
    kd.ef1 <- read_tsv(
      kd.pth %>% str_subset('edgeFactor_1.results.txt'),  
      col_types = cols())
    ef1.top <- read_tsv(
      kd.pth %>% str_subset('edgeFactor_1.tophits.txt'), 
      col_types = cols()) %>% 
      mutate(kd = paste0(NODE,'-',MODULE))
  }
    
  # Join up the results
  kd = bind_rows(
    kd.ef0 %>% mutate(ef = 'ef0_fdr'),
    kd.ef1 %>% mutate(ef = 'ef1_fdr')
    ) %>% 
    mutate(FDR = -log10(FDR)) %>%
    pivot_wider(id_cols = c(MODULE, NODE, MEMBER), 
                names_from = ef, values_from = FDR, values_fill = 0) %>%
    mutate(delta_fdr = ef1_fdr - ef0_fdr) %>% arrange(desc(delta_fdr)) %>% 
    mutate(top = 0, top_ef0 = 0)
  
  # Indicate which driver-module pairs are top for each analysis
  if( any( ef1.top$FDR < 0.05 ) ){
    kd$top[ which(paste0(kd$NODE,'-',kd$MODULE) %in% ef1.top$kd[ef1.top$FDR < 0.05]) ] <- 1
  }
  if( any( ef0.top$FDR < 0.05 ) ){
    kd$top_ef0[ which(paste0(kd$NODE,'-',kd$MODULE) %in% ef0.top$kd[ef0.top$FDR < 0.05]) ] <- 1
  }
  
  return(kd)
}

```

## TREAT-AD data
Grab relevant data from synapse, including:
1) Target Risk Scores ([syn25575156](https://www.synapse.org/#!Synapse:syn25575156){target="_blank"}) and Omics Scores ([syn22758536](https://www.synapse.org/#!Synapse:syn22758536){target="_blank"})  
2) Biodomain Definitions ([syn25428992](https://www.synapse.org/#!Synapse:syn25428992){target="_blank"})  
2) Risk-enriched Biodomain Terms ([syn45824995](https://www.synapse.org/#!Synapse:syn45824995){target="_blank"})
3) Base Network ([syn51110930](https://www.synapse.org/#!Synapse:syn51110930){target="_blank"})  
4) Synapse IDs of path-traced NW objects  
5) Synapse IDs of wKDA results 
6) CRISPRbrain simple phenotype screen data  

```{r}
synLogin()

# target risk scores
scores <- read_csv(
  synTableQuery('select * from syn25575156', includeRowIdAndRowVersion = F)$filepath
  , col_types = cols())
omics <- read_csv(
  synTableQuery('select * from syn22758536', includeRowIdAndRowVersion = F)$filepath
  , col_types = cols())
npath <- read_csv(
  synTableQuery('select * from syn32288310', includeRowIdAndRowVersion = F)$filepath
  , col_types = cols())

agora <- read_csv(synGet('syn12540368')$path, quote = '"', col_types = cols())

# biological domain annotations
biodom <- full_join(
  # biodomains
  readRDS(synGet('syn25428992')$path),
  # domain labels
  read_csv(synGet('syn26856828')$path, col_types = cols()),
  by = c('Biodomain'='domain')
) %>%
  mutate(Biodomain = case_when(Biodomain == 'none' ~ NA_character_, T ~ Biodomain))

domains = biodom %>% pull(Biodomain) %>% unique() %>% sort()

# enriched biodomain terms
enr.bd <- synGet('syn52749187') %>% .$path %>% readRDS() %>% 
  filter(score == 'Overall') %>% select(anno) %>% unnest(anno) %>% 
  mutate(leadingEdge_genes = str_split(core_enrichment, '\\|'))

# base network
base_net <- igraph::read_graph(synGet('syn51110930')$path, format = 'graphml') 

# filt node & edge
tmp <- igraph::delete_vertices(
  base_net,
  igraph::V(base_net)[ igraph::V(base_net)$brain_exp == 0 ]
)
undir_node_edge <- igraph::subgraph.edges(
  tmp,
  igraph::E(tmp)[ igraph::E(tmp)$n_edge_evidence > 1 ],
  delete.vertices = T 
)

# specify directed edge types
directed_edge_types = c("catalysis-precedes",
                        "controls-expression-of",
                        "controls-phosphorylation-of",
                        "controls-state-change-of",
                        "controls-transport-of"
                        )
```

## CRISPRbrain data 
```{r warning=FALSE}
synLogin()

# CRISPRbrain data
syn.dir <- synGetChildren('syn51183357')$asList() %>% 
  tibble(f = .) %>% 
  unnest_wider(f)

# Simple Screens
simple <- map_dfr(
  syn.dir %>% with(which( !grepl('RNA|CROP',name) )),
  ~ { 
    id = syn.dir$id[.x]
    n = syn.dir$name[.x]
    synGet(id)$path %>% 
      read_csv( col_types = cols() ) %>% 
      mutate(cell = n %>% str_split_fixed(.,'-(?!M)', 2) %>% .[,1],
             mode = n %>% str_extract('CRISPR[ain]'),
             expt = n %>% str_remove_all('-CRISPR[ain].csv') %>% 
               str_split_fixed('-(?!M)',2) %>% .[,2] ) %>% 
      relocate(cell, mode, expt)
  }
  ) %>% 
  rename(pval = `P Value`, pheno = `Phenotype`, gene_score = `Gene Score`)

simple <- tibble(expt = simple$expt %>% unique() %>% sort(),
                 phenotype = c('Expansion (CD34 Staining)',
                                'Reactive Oxygen Species (CellRox Intensity)',
                                'Proliferation (CFSE Staining)',
                                'Survival (14 day)', 'Survival (21 day)', 'Survival (28 day)',
                                'Labile Iron (FeRhoNox Intensity)',
                                'Immune Activation (CD38 levels)',
                                'Lysosome Exocytosis (cell surface LAMP1), +IL1a +TNF +C1q',
                                'Lysosome Exocytosis (cell surface LAMP1), Vehicle',
                                'Peroxidized Lipids (Liperfluo intensity)',
                                'Lysosome (LysoTracker intensity)',
                                'Lysosome Mass or pH (LysoTracker staining), +IL1a +TNF +C1q',
                                'Lysosome Mass or pH (LysoTracker staining), Vehicle',
                                'Survival, no antioxidants',
                                'Phagocytosis (pHRodo-rat synaptosomes)',
                                'Phagocytosis (pHRodo-labeled synaptosomes), +IL1a +TNF +C1q',
                                'Phagocytosis (pHRodo-labeled synaptosomes), Vehicle',
                                'Survival, PSAP KO & no antioxidants',
                                'Survival, PSAP KO',
                                'Survival',
                                'Survival-Proliferation',
                                'Inflammatory activation (cell-surface VCAM1 levels), +IL1a +TNF +C1q')
                 ) %>% left_join(simple, . , by = 'expt')

# filter(cell %in% c('iAstrocyte','Glutamatergic Neuron','iTF-Microglia','iPSC')) # don't consider HSPC or T-cell
```

## NW & KDA data

read results from synapse  
```{r}
synLogin()

subdoms  <-  read_syn_dir('syn52314422') %>%  # biodomain
  filter(grepl('Folder', type)) %>% 
  select(bd = name, bd_id = id) %>% 
  rowwise() %>% 
  mutate( sd = read_syn_dir(bd_id) %>% list() ) %>% 
  unnest(sd) %>% 
  select(bd, bd_id, sd = name, sd_id = id) %>% 
  rowwise() %>% 
  mutate(
    nw.dir = read_syn_dir(sd_id) %>% list()
    )
```

```{r}
nw.dat = subdoms %>% select(bd, sd, nw.dir) %>% 
  unnest(nw.dir) %>% filter(grepl('graphml',name)) %>%
  mutate(filt = if_else(grepl('bdFilt',name), 'bd.filt','full')) %>% 
  select(bd,sd,id,filt) %>% 
  pivot_wider(names_from=filt, values_from = id)

# query genes
nw.dat$q_genes <- map(
  1:nrow(nw.dat),
  ~ subdoms$nw.dir[[.x]] %>% filter( grepl('queryList', name) ) %>% 
    pull(id) %>% synGet(.) %>% .$path %>% 
    read_tsv(., col_names = F, col_types = cols()) %>% 
    pull(X1) 
)

# BD filtered NW stats
# future::plan('multisession')
x = furrr::future_map_dfr(
  1:nrow(nw.dat),
  ~{synLogin()
    nw = synGet(nw.dat$bd.filt[.x]) %>% .$path %>% 
      read_graph(., format = 'graphml')
    snw = igraph::simplify(nw, remove.multiple = T)
    tibble(
      avg_node_degree = degree(snw, V(snw)) %>% mean(),
      avg_path_length = snw %>% average.path.length,
      assortativity_coef = snw %>% assortativity(., types1 = V(.)),
      connected_components = snw %>% no.clusters,
      edge_t = e_info(nw) %>% list(),
      node_t = v_info(nw) %>% list()
    )
  }
)
# future::plan('sequential')

nw.dat = bind_rows(
  bind_cols(nw.dat, x) %>% mutate(filt = 'bd.filt')
  # , bind_cols(nw.dat, y) %>% mutate(filt = 'full')
); #rm(x,y)

nw.dat$input = map(
  1:nrow(nw.dat),
  ~ nw.dat$node_t[[.x]] %>% filter(node_status == 'query') %>% pull(name) %>% unique() %>% list()
)

nw.dat$added = map(
  1:nrow(nw.dat),
  ~ nw.dat$node_t[[.x]] %>% filter(node_status == 'added') %>% pull(name) %>% unique() %>% list()
)

nw.dat$nodes = map(
  1:nrow(nw.dat),
  ~ nw.dat$node_t[[.x]] %>% pull(name) %>% unique() %>% list()
)

nw.dat$edges = map(
  1:nrow(nw.dat),
  ~ nw.dat$edge_t[[.x]] %>% pull(edge) %>% unique() %>% list()
)

nw.dat <- relocate(nw.dat, filt, .after = 'bd.filt')
nw.dat <- relocate(nw.dat, q_genes, .after = 'node_t')
```

# KD Modules in Graphs

Compare the distributions between filtered base network and traced subdomain networks  
```{r}
modules <- read_tsv(
  here::here('results','subdomain',
             'module_representation_across_networks.tsv'),
  col_types = cols()
  )

tmp <- modules %>% 
  pivot_longer(cols = 7:ncol(modules)) %>% 
  mutate( 
    # biodom_nw = value
    # , n_nw = (biodom_nw/100)*n_symbol
    # , base_nw = node_edge_filt
    
    subdom_nw = 100*(value / n_symbol)
    , base_nw = 100*(node_edge_filt / n_symbol)
          ) %>%
  # left_join(., subdoms %>% select(bd, name = sd)) %>% 
  rename(sd = name, n_nw = value) %>% 
  pivot_longer(cols = c(subdom_nw, base_nw)) %>% 
  rename(pct = value) %>% 
  filter(n_nw >= 3, pct > 0)

```

```{r}
ggplot(tmp, aes(pct) )+
  geom_density(aes(fill = name), alpha = .5)+
  labs(x = '% GO term genes in NW', 
       subtitle = 'distribution of all terms >0% and >=3 genes in each NW class')
```
# Key Driver Analysis 

```{r echo=FALSE,warning=FALSE,message=FALSE,results='asis', fig.width=10, fig.height=8}
synLogin()

for(parent_dom in unique(subdoms$bd)){
  
  cat("  \n##", parent_dom, " \n")
  
  for(dom in subdoms$sd[which(subdoms$bd == parent_dom)]){
  
    # Get NW info
    nw <- subdoms %>% 
      filter(bd == parent_dom, sd == dom) %>% 
      pull(nw.dir) %>% .[[1]] %>% 
      filter(grepl('bdFilt.+graphml',name)) %>% 
      pull(id) %>% synGet(.) %>% .$path %>% 
      read_graph(., format = 'graphml')
    
    nodes <- v_info(nw)
    edges <- e_info(nw)
    
    snw <- igraph::simplify(nw, remove.multiple = T)
    
    # tabulate GO term representation across NW
    nw_terms <- biodom %>% 
      filter(!is.na(n_symbol),n_symbol > 0) %>% 
      select(Biodomain, MODULE = GOterm_Name, NODE = symbol, n_symbol) %>% 
      rowwise() %>% 
      mutate(
        n_nw = length( intersect( NODE, nodes$name ) ),
        pct_term = 100*(n_nw/n_symbol)
      ) %>% 
      distinct()
    
    # get KDA results and annotate
    kd.res <- subdoms %>%       
      filter(bd == parent_dom, sd == dom) %>% 
      pull(nw.dir) %>% .[[1]] %>% filter(name == 'kda') %>% 
      pull(id) %>% read_kd(.)
    
    if( is.null(kd.res) ){
      cat("  \n###", dom, " {.tabset}  \n")
      cat('Not a complete results set','\n')
      next
    }
    
    kd.res <- kd.res %>% 
      left_join(
        ., nodes %>% select(NODE = name, node_status)
      ) %>% 
      left_join(
        ., biodom %>% select(MODULE = GOterm_Name, Biodomain, abbr:color) 
      ) %>% 
      left_join(
        ., nw_terms %>% select(MODULE, n_symbol:pct_term) %>% distinct()
      ) 
    
    top.kd <- kd.res %>% 
      filter(ef1_fdr > -log10(0.05), delta_fdr > 0, top == 1, pct_term > 50) 
    
    kd.hits <- top.kd %>% pull(NODE) %>% unique()
    
    # tabulate top biodoms in KD results
    kd.biodoms <- top.kd %>% 
      mutate(pair = paste0(NODE,':',MODULE)) %>% 
      group_by(Biodomain) %>% 
      summarise(n_term = length(unique(MODULE)),
                n_node = length(unique(NODE)),
                n_kd = length(unique(pair)),
                # terms = list(unique(MODULE)),
                min_fdr = signif( 10^-max(ef1_fdr), digits = 3),
                max_delta = signif( max(delta_fdr), digits = 3) ) %>% 
      full_join(., 
                biodom %>% group_by(Biodomain) %>% mutate(n_go = length(unique(GO_ID))) %>% 
                  select(Biodomain, n_go, abbr:color) %>% distinct(), 
                by = 'Biodomain') %>% 
      ungroup() %>%
      mutate(fxn_bd_term = n_term / n_go) %>% 
      filter( !is.na(Biodomain) ) %>% 
      mutate(across(.cols = c(n_term:n_kd), ~if_else(is.na(.x), as.integer(0), .x))) 
    
    ##
    # CBrain phenotype associations with KDs
    if( length(kd.hits) > 0){
      
      cbrain_lr <- simple %>%
        mutate(cb_hit = if_else( `Hit Class` == 'Non-Hit', 0, 1)) %>%
        select(cell, mode, expt, Gene, cb_hit) %>% distinct() %>%
        mutate(kd = if_else(Gene %in% kd.hits, 1, 0)) %>%
        left_join(., tibble(Gene = names(V(snw)), node_degree = degree(snw)) ) %>%
        filter(!is.na(node_degree)) %>%
        group_by(cell,mode,expt) %>%
        mutate(
          lr = glm( cb_hit~kd+node_degree,
                    family=binomial(link='logit')) %>% broom::tidy() %>%
                 filter(term == 'kd') %>%
                 mutate(nobs = glm( cb_hit~kd+node_degree,
                                    family=binomial(link='logit')) %>%
                          broom::glance() %>% pull(nobs)) %>% list()
          ) %>%
        unnest(lr)  %>%
        select(cell, mode, expt, p.value, nobs, estimate, statistic ) %>% distinct() %>%
        arrange(p.value)
    
    } else { cbrain_lr = data.frame() } 
    
    #  CRISPRbrain -- linear regression
    tmp <- top.kd %>% inner_join( simple,., by =c('Gene'='NODE')) %>%
      left_join(., tibble(Gene = names(V(snw)), node_degree = degree(snw)) ) %>%
      mutate(node_degree = scale(node_degree, center = T, scale = T) %>% c(),
             ef1_fdr = scale(ef1_fdr, center = T, scale = T) %>% c(),
             delta_fdr = scale(delta_fdr, center = T, scale = T) %>% c(),
             gs = scale(abs(gene_score), center = T, scale = T) %>% c()
             ) %>% 
      select(Gene, MODULE, cell, mode, expt, gs, ef1_fdr, delta_fdr, node_degree) %>% 
      distinct()
  
    if( nrow(tmp) > 0 & !all(is.nan(tmp$ef1_fdr)) ){
      cbrain_lm_ef1 <- tmp %>%
        group_by(cell,mode,expt) %>%
        mutate(
          lm = if_else(
            length(unique(Gene)) <= 2 ,
            tibble(estimate = NA, statistic = NA, p.value = NA, r.squared = NA, nobs = NA) %>% list(),
            lm(gs~ef1_fdr+node_degree) %>% broom::tidy() %>% filter(term == 'ef1_fdr') %>%
              mutate(r.squared = lm(gs~ef1_fdr+node_degree) %>% broom::glance() %>% pull(r.squared),
                     nobs = lm(gs~ef1_fdr+node_degree) %>% broom::glance() %>% pull(nobs)) %>% list()
          , )
            ) %>%
        unnest(lm)  %>%
        select(cell, mode, expt, p.value, r.squared, nobs, estimate, statistic ) %>% distinct() %>%
        arrange(p.value) 
    
      cbrain_lm_delta <- tmp %>%
        group_by(cell,mode,expt) %>%
        mutate(
          lm = if_else(
            length(unique(Gene)) <= 2 ,
            tibble(estimate = NA, statistic = NA, p.value = NA, r.squared = NA, nobs = NA) %>% list(),
            lm(gs~delta_fdr+node_degree) %>% broom::tidy() %>% filter(term == 'delta_fdr') %>%
              mutate(r.squared = lm(gs~delta_fdr+node_degree) %>% broom::glance() %>% pull(r.squared),
                     nobs = lm(gs~delta_fdr+node_degree) %>% broom::glance() %>% pull(nobs)) %>% list()
          )
            ) %>%
        unnest(lm)  %>%
        select(cell, mode, expt, p.value, r.squared, nobs, estimate, statistic ) %>% distinct() %>%
        arrange(p.value)
    } else {
      
    cbrain_lm_ef1 <- data.frame()
    cbrain_lm_delta <- data.frame()
    
    }

    ##
    # PLOTS
    biodoms_plot <- kd.biodoms %>% 
      pivot_longer(n_kd) %>% 
      mutate(Biodomain = fct_reorder(Biodomain, value)) %>% 
      ggplot(aes(value, Biodomain))+
      geom_segment(aes(yend=Biodomain, xend=0), color = 'grey50')+
      geom_point(aes(size = max_delta, color = color))+
      scale_color_identity()+
      labs(y='', 
           x = '# KDs\n(NODE-MODULE pair)',
           #title = paste0(dom, ' Network Key Drivers'),
           subtitle = 'Biodomain GO terms')+ 
      theme(legend.position = 'right')
      # +facet_wrap(~name)
  
    if(nrow(top.kd) > 0){
      
      all_res <- kd.res %>% 
        ggplot(aes( ef1_fdr, delta_fdr ))+
        labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', title = dom)+
        geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
        geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
        geom_point(alpha = .2, size = 1, aes(color = color, shape = node_status) )+
        geom_point(data = subset(kd.res, top == 1 & ef1_fdr > -log10(0.05) 
                                 & delta_fdr > 0 & pct_term > 50)
                   , alpha = .6, size = 3, aes(color = color, shape = node_status))+
        scale_color_identity(guide = 'none')+
        ggrepel::geom_label_repel(
          data = subset( kd.res, top == 1 & ef1_fdr > -log10(0.05)
                         & delta_fdr > 0 & pct_term >50
                         # & MODULE %in% enr.bd$pathway[which( enr.bd$padj < 0.05
                         #    # & enr.bd$Biodomain == str_replace_all(dom, '_', ' ')
                         #                              )]
                         ),
          aes(label = paste0(NODE, '\n', MODULE, '\n', Biodomain)),
          size = 2, alpha = .7, min.segment.length = 0)
  
      top_res <- top.kd %>% 
        ggplot(aes( ef1_fdr, delta_fdr ))+
        labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', 
             title = dom,
             subtitle = 'signif KDs (EF1 FDR < 0.05), \u0394 FDR > -1'
             )+
        # geom_abline(intercept = 0, slope =1, lty= 2, lwd = .5)+
        geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
        geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
        geom_point(alpha = .6, size = 2, shape = 21, color = 'grey20', aes(fill = color))+
        # ggrepel::geom_label_repel(
        #   data = subset( top.kd, MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]),
        #   aes(label = paste0(NODE, '\n', MODULE, '\n', Biodomain)),
        #   size = 2, alpha = .7, min.segment.length = 0)+
        facet_wrap(~Biodomain)+ #, scales = 'free'
        scale_fill_identity(guide = 'none') #; plotly::ggplotly(p)
      
      top_dt <- top.kd %>% 
        filter(MODULE %in% enr.bd$pathway[enr.bd$padj < 0.05]) %>% 
        select(NODE, node_status, MODULE, pct_term, Biodomain, MEMBER, ef1_fdr, delta_fdr) %>% 
        mutate(MODULE = str_trunc(MODULE, 25, 'right'),
               #ef0_fdr = signif(ef0_fdr, digits = 3),
               ef1_fdr = signif(ef1_fdr, digits = 3),
               delta_fdr = signif(delta_fdr, digits = 3)) %>% 
        arrange(desc(delta_fdr), desc(ef1_fdr)) %>% 
        slice_head(n = 25)
  
      kd.nodes <- top.kd %>% 
        select(NODE, node_status, MODULE, Biodomain, 
               MEMBER, top, contains('fdr')) %>% 
        arrange(desc(delta_fdr), desc(ef1_fdr)) %>%
        group_by(NODE) %>% 
        summarise(n_biodom = length(unique(Biodomain))
               , n_term = length(unique(MODULE))
               , ef1_max = max(ef1_fdr)
               , delta_max = max(delta_fdr)) 
      
      vert_num <- match(kd.nodes$NODE, V(snw)$name)
      vert_neigh <- neighbors(snw, vert_num)
      
      g3 <- induced_subgraph(snw, c(vert_num, vert_neigh))
      unlinked <- names(degree(g3)[which(degree(g3)==0)])
      g3 <- delete.vertices(g3, unlinked)
      
      # KD evidence
      x = tibble( node = V(g3) %>% names ) %>% 
        left_join(., kd.nodes, by = c('node'='NODE')) %>% 
        mutate(kd = if_else(is.na(n_term), 0, 1))
      for(i in 2:ncol(x)){
        igraph::vertex_attr(g3, names(x)[i], index = igraph::V(g3)) <- x %>% pull(i)
      }
      
      kd_nw <- ggraph(g3, layout = 'graphopt') +
        geom_edge_link(alpha = .3, color = 'grey90') +
        geom_node_point( shape = 21, color = "black", alpha = .3, fill = 'grey90', 
                         aes(filter= .N()$kd == 0)  )+
        geom_node_point( color = "black", alpha = .6, 
                         aes(size = delta_max, fill = ef1_max, shape=node_status, 
                             filter = .N()$kd == 1) )+
        scale_shape_manual(name='Node Source', breaks=c('added', 'query'),
                           values=c('added'=23, 'query'=21))+
        scale_size_continuous(range = c(3,12))+
        geom_node_text(aes(label = name, filter = .N()$kd == 1), size = 2) +
        viridis::scale_fill_viridis()+
        theme_graph(background = 'white')
    
    } else {
      
      all_res <- kd.res %>% 
        ggplot(aes( ef1_fdr, delta_fdr ))+
        labs(x = 'wKDA FDR ef1, -log10', y = '\u0394 FDR, ef1 - ef0', title = dom)+
        geom_smooth(method = 'glm', lty = 2, lwd = .5, color = 'grey20')+
        geom_vline(xintercept = 0, lwd = .5)+ geom_hline(yintercept = 0, lwd = .5) +
        geom_point(alpha = .2, size = 1, aes(color = color, shape = node_status) )+
        geom_point(data = subset(kd.res, top == 1 & ef1_fdr > -log10(0.05) 
                                 & delta_fdr > 0 & pct_term > 50)
                   , alpha = .6, size = 3, aes(color = color, shape = node_status))+
        scale_color_identity(guide = 'none')
      
      df <- data.frame()
  
      top_res <- ggplot(df) + geom_point() + xlim(0, 10) + ylim(0, 100)
      top_dt <- ggplot(df) + geom_point() + xlim(0, 10) + ylim(0, 100)
      kd_nw <- ggplot(df) + geom_point() + xlim(0, 10) + ylim(0, 100)
    }
    
    cat("  \n###", dom, " {.tabset}  \n")
    
    cat("  \n#### All KD results  \n")
    
    res = cowplot::plot_grid(all_res, biodoms_plot, rel_widths = c(1,.7), nrow = 1)
    plot(res)
    
    plot.new()
    dev.off()
    cat("  \n  \n")  
    
    cat('\n#### Top Key Drivers: \n')
    plot(top_res)
    if(nrow(top.kd) > 0){ print(top_dt) }
    
    plot.new()
    dev.off()
    cat("  \n  \n")  
    
    cat('\n#### Key Driver Nodes: \n')
    plot(kd_nw)
    
    plot.new()
    dev.off()
    cat("  \n  \n")  
    
    cat('\n#### CRISPRbrain overlap \n')
    cat('\n logit: cbrain hit ~ key driver + node degree \n')
    print( cbrain_lr )
    cat('\n lm: abs(gene_score) ~ ef1_fdr + node_degree \n')
    print( cbrain_lm_ef1 )
    cat('\n lm: abs(gene_score) ~ delta_fdr + node_degree \n')
    print( cbrain_lm_delta )
    plot.new()
    dev.off()
    cat("  \n  \n")  

  }

}
```


```{r}
  # # CRISPRbrain -- logistic regression
  # cbrain_lr <- simple %>%
  #   mutate(cb_hit = if_else( `Hit Class` == 'Non-Hit', 0, 1)) %>%
  #   select(cell, mode, expt, Gene, cb_hit) %>% distinct() %>%
  #   mutate(kd = if_else(Gene %in% kd.hits, 1, 0)) %>%
  #   left_join(., tibble(Gene = names(V(snw)), node_degree = degree(nw)) ) %>%
  #   filter(!is.na(node_degree)) %>%
  #   group_by(cell,mode,expt) %>%
  #   mutate(
  #     lr = glm( cb_hit~kd+node_degree,
  #               family=binomial(link='logit')) %>% broom::tidy() %>%
  #            filter(term == 'kd') %>%
  #            mutate(nobs = glm( cb_hit~kd+node_degree,
  #                               family=binomial(link='logit')) %>%
  #                     broom::glance() %>% pull(nobs)) %>% list()
  #     ) %>%
  #   unnest(lr)  %>%
  #   select(cell, mode, expt, estimate, statistic, p.value, nobs) %>% distinct() %>%
  #   # filter(p.value < 0.05) %>%
  #   arrange(p.value)
  # 
  # # cbrain_lr_dt <- cbrain_lr %>%
  # #   select(cell:expt, estimate:p.value) %>%
  # #   DT::datatable(rownames = F, filter = 'top', caption = 'cb_hit ~ kd + node_degree',
  # #                 options = list(pageLength = 6)) %>% #
  # #   DT::formatSignif(columns = c('estimate', 'std.error','statistic', 'p.value'))
  # 
  # #  CRISPRbrain -- linear regression
  # tmp <- top.kd %>% inner_join( simple,., by =c('Gene'='NODE')) %>%
  #   left_join(., tibble(Gene = names(V(snw)), node_degree = degree(snw)) ) %>%
  #   mutate(node_degree = scale(node_degree, center = T, scale = T),
  #          ef1_fdr = scale(ef1_fdr, center = T, scale = T),
  #          delta_fdr = scale(delta_fdr, center = T, scale = T)
  #          )
  # 
  # cbrain_lm_ef1 <- tmp %>%
  #   group_by(cell,mode,expt) %>%
  #   mutate(gs = scale(abs(gene_score), center = T, scale = T),
  #          lm = lm(gs~ef1_fdr+node_degree) %>% broom::tidy() %>%
  #            filter(term == 'ef1_fdr') %>%
  #            mutate(r.squared = lm(abs(gene_score)~ef1_fdr+node_degree) %>%
  #                     broom::glance() %>% pull(r.squared),
  #                   nobs = lm(abs(gene_score)~ef1_fdr+node_degree) %>%
  #                     broom::glance() %>% pull(nobs)) %>% list()) %>%
  #   unnest(lm)  %>%
  #   select(cell, mode, expt,  estimate, statistic, p.value, r.squared, nobs) %>% distinct() %>%
  #   arrange(p.value) 
  # # %>%
  # #   DT::datatable(rownames = F, filter = 'top',
  # #                 caption = 'abs(gene_score) ~ ef1_fdr + node_degree',
  # #                 options = list(pageLength = 6)) %>% #
  # #   DT::formatSignif(columns = c('statistic', 'std.error',
  # #                                'r.squared', 'p.value', 'estimate'))
  # 
  # cbrain_lm_delta <- tmp %>%
  #   group_by(cell,mode,expt) %>%
  #   mutate(gs = scale( abs(gene_score), center = T, scale = T),
  #          lm = lm(gs~delta_fdr+node_degree) %>% broom::tidy() %>%
  #            filter(term == 'delta_fdr') %>%
  #            mutate(r.squared = lm(gs~delta_fdr+node_degree) %>%
  #                     broom::glance() %>% pull(r.squared),
  #                   nobs = lm(gs~delta_fdr+node_degree) %>%
  #                     broom::glance() %>% pull(nobs)) %>% list()) %>%
  #   unnest(lm)  %>%
  #   select(cell, mode, expt, estimate, statistic, p.value, r.squared, nobs) %>% distinct() %>%
  #   # filter(p.value < 0.05) %>%
  #   arrange(p.value)
  # # %>%
  # #   DT::datatable(rownames = F, filter = 'top',
  # #                 caption = 'abs(gene_score) ~ \u0394 fdr (ef1-ef0) + node_degree',
  # #                 options = list(pageLength = 6)) %>% #
  # #   DT::formatSignif(columns = c('statistic', 'std.error',
  # #                                'r.squared', 'p.value', 'estimate'))
```

# Session
```{r}
sessionInfo()  
```

