---
title: "Biodomain NW & Key Drivers"
author: "Greg Cary"
date: "`r Sys.Date()`"
output: 
  html_document: 
    fig_width: 5
    fig_height: 4
  html_notebook:
    code_folding: hide
    theme: readable
    css: style.css
    toc: true
    toc_float: true
---
# Setup

```{r setup}
# # Package names
# packages <- c(
#   # 'paxtoolsr','org.Hs.eg.db','HotNetvieweR','clusterProfiler', 
#   'synapser','igraph','tidygraph','ggraph','tidyverse'
#   )
# 
# # Load packages
# invisible(lapply(packages, library, character.only = TRUE))

library(synapser)
library(igraph)
library(tidygraph)
library(ggraph)
library(tidyverse)

source('../../treatAD_biodomains/scripts/biodom_tally.R')
source('../../treatAD_biodomains/scripts/annotate_enr_term_biodomains.R')
source('../../treatAD_biodomains/scripts/biodom_enr_plots.R')

theme_set(theme_bw())
```

# Data
Grab relevant data from synapse, including:
1) Target Risk Scores ([syn25575156](https://www.synapse.org/#!Synapse:syn25575156){target="_blank"}) and Omics Scores ([syn22758536](https://www.synapse.org/#!Synapse:syn22758536){target="_blank"})  
2) Biodomain Definitions ([syn25428992](https://www.synapse.org/#!Synapse:syn25428992){target="_blank"})  
2) Risk-enriched Biodomain Terms ([syn45824995](https://www.synapse.org/#!Synapse:syn45824995){target="_blank"})
3) Base Network ([syn51110930](https://www.synapse.org/#!Synapse:syn51110930){target="_blank"})  
4) Synapse IDs of path-traced NW objects  
5) Synapse IDs of wKDA results 
6) CRISPRbrain simple phenotype screen data  

```{r}
synLogin()

# target risk scores
scores <- read_csv(
  synTableQuery('select * from syn25575156', includeRowIdAndRowVersion = F)$filepath
  , col_types = cols())
omics <- read_csv(
  synTableQuery('select * from syn22758536', includeRowIdAndRowVersion = F)$filepath
  , col_types = cols())

# biological domain annotations
biodom <- full_join(
  # biodomains
  readRDS(synGet('syn25428992')$path),
  # domain labels
  read_csv(synGet('syn26856828')$path, col_types = cols()),
  by = c('Biodomain'='domain')
) %>%
  mutate(Biodomain = case_when(Biodomain == 'none' ~ NA_character_, T ~ Biodomain))

domains = biodom %>% pull(Biodomain) %>% unique() %>% sort()

# enriched biodomain terms
enr.bd <- read_csv( synGet('syn45824995')$path, col_types = cols() ) %>% 
  mutate(leadingEdge_genes = str_split(leadingEdge_genes, '\\|'))

# base network
base_net <- igraph::read_graph(synGet('syn51110930')$path, format = 'graphml') 

# specify directed edge types
directed_edge_types = c("catalysis-precedes",
                        "controls-expression-of",
                        "controls-phosphorylation-of",
                        "controls-state-change-of",
                        "controls-transport-of"
                        )
```

pre-filtered NWs    
```{r}
undir <- base_net

# filt node & edge
tmp <- igraph::delete_vertices(
  base_net,
  igraph::V(base_net)[ igraph::V(base_net)$brain_exp == 0 ]
)
undir_node_edge <- igraph::subgraph.edges(
  tmp,
  igraph::E(tmp)[ igraph::E(tmp)$n_edge_evidence > 1 ],
  delete.vertices = T 
)

# filt node
undir_node <- igraph::delete_vertices(
    base_net,
    igraph::V(base_net)[ igraph::V(base_net)$brain_exp == 0 ]
  )

# filt edge
undir_edge <- igraph::subgraph.edges(
    base_net,
    igraph::E(base_net)[ igraph::E(base_net)$n_edge_evidence > 1 ],
    delete.vertices = T 
  )

# dir
dir <- igraph::subgraph.edges( 
    base_net, 
    igraph::E(base_net)[ igraph::E(base_net)$directed == 1 ],
    delete.vertices = T 
  ) %>% 
    as.directed(mode = 'arbitrary')

# dir node edge
dir_node_edge <- igraph::subgraph.edges( 
    undir_node_edge, 
    igraph::E(undir_node_edge)[ igraph::E(undir_node_edge)$directed == 1 ],
    delete.vertices = T 
  ) %>% 
    as.directed(mode = 'arbitrary')

# dir node
dir_node <- igraph::subgraph.edges( 
    undir_node, 
    igraph::E(undir_node)[ igraph::E(undir_node)$directed == 1 ],
    delete.vertices = T 
  ) %>% 
    as.directed(mode = 'arbitrary')

# dir edge
dir_edge <- igraph::subgraph.edges( 
    undir_edge, 
    igraph::E(undir_edge)[ igraph::E(undir_edge)$directed == 1 ],
    delete.vertices = T 
  ) %>% 
    as.directed(mode = 'arbitrary')

```

## cbrain data
Read CRISPRbrain phenotype data 
```{r warning=FALSE}
synLogin()

# CRISPRbrain data
syn.dir <- synGetChildren('syn51183357')$asList() %>% 
  tibble(f = .) %>% 
  unnest_wider(f)

# Simple Screens
simple <- map_dfr(
  syn.dir %>% with(which( !grepl('RNA|CROP',name) )),
  ~ { 
    id = syn.dir$id[.x]
    n = syn.dir$name[.x]
    synGet(id)$path %>% 
      read_csv( col_types = cols() ) %>% 
      mutate(cell = n %>% str_split_fixed(.,'-(?!M)', 2) %>% .[,1],
             mode = n %>% str_extract('CRISPR[ain]'),
             expt = n %>% str_remove_all('-CRISPR[ain].csv') %>% 
               str_split_fixed('-(?!M)',2) %>% .[,2] ) %>% 
      relocate(cell, mode, expt)
  }
  ) %>% 
  rename(pval = `P Value`, pheno = `Phenotype`, gene_score = `Gene Score`)

simple <- tibble(expt = simple$expt %>% unique() %>% sort(),
                 phenotype = c('Expansion (CD34 Staining)',
                                'Reactive Oxygen Species (CellRox Intensity)',
                                'Proliferation (CFSE Staining)',
                                'Survival (14 day)', 'Survival (21 day)', 'Survival (28 day)',
                                'Labile Iron (FeRhoNox Intensity)',
                                'Immune Activation (CD38 levels)',
                                'Lysosome Exocytosis (cell surface LAMP1), +IL1a +TNF +C1q',
                                'Lysosome Exocytosis (cell surface LAMP1), Vehicle',
                                'Peroxidized Lipids (Liperfluo intensity)',
                                'Lysosome (LysoTracker intensity)',
                                'Lysosome Mass or pH (LysoTracker staining), +IL1a +TNF +C1q',
                                'Lysosome Mass or pH (LysoTracker staining), Vehicle',
                                'Survival, no antioxidants',
                                'Phagocytosis (pHRodo-rat synaptosomes)',
                                'Phagocytosis (pHRodo-labeled synaptosomes), +IL1a +TNF +C1q',
                                'Phagocytosis (pHRodo-labeled synaptosomes), Vehicle',
                                'Survival, PSAP KO & no antioxidants',
                                'Survival, PSAP KO',
                                'Survival',
                                'Survival-Proliferation',
                                'Inflammatory activation (cell-surface VCAM1 levels), +IL1a +TNF +C1q')
                 ) %>% left_join(simple, . , by = 'expt')

# filter(cell %in% c('iAstrocyte','Glutamatergic Neuron','iTF-Microglia','iPSC')) # don't consider HSPC or T-cell
```

## NW & KDA data

read results from synapse  
```{r}
# top level biodom directory
doms <- synGetChildren('syn51739831')$asList() %>%
  tibble(f = .) %>% unnest_wider(f) %>%
  filter( !(name %in% c('pseudotime','nanostring_induced_subgraph.graphml', 'key_drivers_all_nw.csv')) ) %>%
  select(bd = name, id) %>% 
  arrange(bd) %>% 
  mutate(i = 1:nrow(.)) %>% 
  rowwise() %>% 
  mutate(
    nw.dir = synGetChildren(  parent = id  )$asList() %>% tibble(f = .) %>% unnest_wider(f) %>% list(),
    kd.dir = synGetChildren(  parent = nw.dir$id[grepl('kda',nw.dir$name)]  )$asList() %>% tibble(f = .) %>% unnest_wider(f) %>% list()
    )

```

<!-- ```{r} -->

<!-- # read NW results dir on Synapse -->
<!-- nw.dirs <- map_dfr( -->
<!--   synGetChildren('syn51739831')$asList() %>% -->
<!--     tibble(f = .) %>% unnest_wider(f) %>% -->
<!--     filter( -->
<!--       !(name %in% c('pseudotime','nanostring_induced_subgraph.graphml', 'key_drivers_all_nw.csv')) -->
<!--       ) %>% -->
<!--     pull(id), -->
<!--   ~{ synGetChildren(  parent = .x  )$asList() %>% -->
<!--       tibble(f = .) %>% unnest_wider(f) %>% -->
<!--       filter(grepl('graphml', name)) %>% -->
<!--       mutate( -->
<!--         bd = str_extract(name, '^(?<=[bdFiltered_]{0,1}).+(?=_[un]*directed)') %>% -->
<!--           str_remove_all('bdFiltered_') %>% str_replace_all('_',' '), -->
<!--         bd.filt = if_else(grepl('bdFiltered',name),T,F), -->
<!--         filt = str_extract(name, '(?<=_filt_).+(?=\\.graphml)'), -->
<!--         dir = str_extract(name, '[un]*directed') -->
<!--         ) %>% -->
<!--       relocate(bd, bd.filt, filt, dir) -->
<!--     } -->
<!-- ) %>% -->
<!--   filter(!grepl('Astro|Micro', filt)) -->

<!-- # read KDA results dir on Synapse -->
<!-- kda.dirs <- map_dfr( -->
<!--   synGetChildren('syn51739831')$asList() %>% -->
<!--     tibble(f = .) %>% unnest_wider(f) %>% -->
<!--     filter( -->
<!--       !(name %in% c('pseudotime','nanostring_induced_subgraph.graphml', 'key_drivers_all_nw.csv')) -->
<!--       ) %>% -->
<!--     pull(id), -->
<!--   ~{ id = synGetChildren( parent = .x )$asList() %>% -->
<!--       tibble(f = .) %>% unnest_wider(f) %>% -->
<!--       filter(grepl('kda', name)) %>% pull(id) -->

<!--      bd = synGet(.x)$properties$name -->

<!--      synGetChildren(id)$asList() %>% -->
<!--        tibble(f = .) %>% unnest_wider(f) %>% -->
<!--        filter(grepl('results|tophits',name)) %>% -->
<!--        mutate( -->
<!--           bd = bd %>% str_replace_all('_' ,' '), -->
<!--           filt = str_extract(name, '(?<=_filt_).+(?=_addWeights)'), -->
<!--           dir = str_extract(name, '[un]*directed'), -->
<!--           ef = str_extract(name, '(?<=_edgeFactor_)[0|1]') -->
<!--           ) %>% -->
<!--         relocate(bd, filt, dir, ef) -->
<!--     } -->
<!-- ) %>% -->
<!--   mutate(set = case_when(grepl('results', name) ~ 'full', grepl('top',name) ~ 'top', T ~ NA_character_)) %>% -->
<!--   relocate(set) %>% -->
<!--   filter(!grepl('Astro|Micro', filt)) -->
<!-- ``` -->

read local results directories
```{r}
# # read local results dir
# doms = list.files('../results/biodomain')
# nw.dirs <- tibble(bd = doms, i = 1:length(doms)) %>% 
#   rowwise() %>% 
#   mutate(
#     f = list.files( paste0('../results/biodomain/',bd) ) %>% list(),
#     kd = list.files( paste0('../results/biodomain/',bd,'/kda') ) %>% list()
#   )
# nw.dirs$kd[[ match('APP_Metabolism', nw.dirs$bd) ]]

# i = which(doms == 'Immune_Response')

# # check which trace / KDA jobs have completed
# nw.dirs %>% rowwise() %>% mutate(n = length(unlist(kd))) %>% arrange(desc(n))
```

## functions

### nw data

```{r}
read_nw <- function(dom_idx){
  
  nw = read.graph(
    synGet(
      doms$nw.dir[[dom_idx]] %>% filter( grepl('bdFiltered.+graphml', name) ) %>% pull(id)
    )$path,
    format = 'graphml'
    )

  return(nw)
  
}
```

<!-- ```{r} -->
<!-- read_nw <- function(dom_idx){ -->
<!--   nw = read.graph( -->
<!--     paste0(here::here(), '/results/biodomain/', doms[dom_idx], '/', -->
<!--            nw.dirs$f[[match(doms[dom_idx], nw.dirs$bd)]] %>% -->
<!--              str_subset(., 'bdFiltered') %>% str_subset('graphml')), -->
<!--     format = 'graphml') -->

<!--   return(nw) -->
<!-- } -->
<!-- ``` -->

### kda data

```{r}
read_kd <- function(dom_idx){

  kd.ef0 <- read_tsv(synGet(doms$kd.dir[[dom_idx]] %>% filter( grepl('edgeFactor_0.results.txt', name) ) %>% pull(id))$path, col_types = cols())
  kd.ef1 <- read_tsv(synGet(doms$kd.dir[[dom_idx]] %>% filter( grepl('edgeFactor_1.results.txt', name) ) %>% pull(id))$path, col_types = cols())
  kd.top <- read_tsv(synGet(doms$kd.dir[[dom_idx]] %>% filter( grepl('edgeFactor_1.tophits.txt', name) ) %>% pull(id))$path, col_types = cols()) %>% 
    mutate(kd = paste0(NODE,'-',MODULE))
    
  kd = bind_rows(
    kd.ef0 %>% mutate(ef = 'ef0_fdr'),
    kd.ef1 %>% mutate(ef = 'ef1_fdr')
    ) %>% 
    mutate(FDR = -log10(FDR)) %>%
    pivot_wider(id_cols = c(MODULE, NODE, MEMBER), names_from = ef, values_from = FDR, values_fill = 0) %>%
    mutate(delta_fdr = ef1_fdr - ef0_fdr) %>% arrange(desc(delta_fdr)) %>% 
    mutate(top = 0)
  
  if( any( kd.top$FDR < 0.05 ) ){
    kd$top[ which(paste0(kd$NODE,'-',kd$MODULE) %in% kd.top$kd[kd.top$FDR < 0.05]) ] <- 1
  }
  
  return(kd)
}

```

<!-- ```{r} -->
<!-- read_kd_local <- function(dom_idx){ -->

<!--   kd.pth <- paste0(here::here(), '/results/biodomain/', doms[dom_idx],'/kda') -->
<!--   kd.res <- list.files(kd.pth, full.names = T) %>% str_subset('results.txt') -->
<!--   kd.top <- list.files(kd.pth, full.names = T) %>% str_subset('tophits.txt') -->

<!--   kd = bind_rows( -->
<!--     read_tsv(kd.res %>% str_subset(.,'edgeFactor_0'), col_types = cols()) %>% mutate(ef = 'ef0_fdr'), -->
<!--     read_tsv(kd.res %>% str_subset(.,'edgeFactor_1'), col_types = cols()) %>% mutate(ef = 'ef1_fdr') -->
<!--     ) %>%  -->
<!--     mutate(FDR = -log10(FDR)) %>% -->
<!--     pivot_wider(id_cols = c(MODULE, NODE, MEMBER), names_from = ef, values_from = FDR, values_fill = 0) %>% -->
<!--     mutate(delta_fdr = ef1_fdr - ef0_fdr) %>% arrange(desc(delta_fdr)) %>%  -->
<!--     mutate(top = 0) -->

<!--   top = read_tsv(kd.top %>% str_subset('edgeFactor_1'), col_types = cols()) %>%  -->
<!--     mutate(kd = paste0(NODE,'-',MODULE)) -->

<!--   if( any( top$FDR < 0.05 ) ){ -->
<!--     kd$top[ which(paste0(kd$NODE,'-',kd$MODULE) %in% top$kd[top$FDR < 0.05]) ] <- 1 -->
<!--   } -->

<!--   return(kd) -->
<!-- } -->

<!-- ``` -->

### plot subnetwork
```{r}
plot_kd_subnet <- function(nw, kd, term) {
  
  vert_num <- match(kd, V(nw)$name)
  
  vert_neigh <- neighbors(nw, vert_num)
  
  term_num <- biodom %>%
    filter(GOterm_Name == term) %>%
    pull(symbol) %>% unlist() %>%
    match(., V(nw)$name) %>% .[!is.na(.)]
  
  g2 <- induced_subgraph(nw, c(vert_num, intersect(term_num, vert_neigh)))
  g3 <- induced_subgraph(nw, c(vert_num, term_num))
  
  cowplot::plot_grid(
    
    ggraph(g3, layout = 'linear', circular = TRUE) +
      geom_edge_arc(alpha = .3, color = 'grey75') +
      geom_node_point( shape = 21, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter= .N()$name != kd)  )+
      geom_node_point( shape = 23, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter = .N()$name == kd) )+
      geom_node_text(aes(label = name), size = 2) +
      coord_fixed() +
      scale_size_continuous( range = c(.5, 10), limits = c(0, 5), trans = 'exp')+
      scale_fill_gradient2(
        low = 'purple', mid = 'grey20', high = 'green', na.value = 'grey85',
        limits = c(-2.5,2.5) )+ #approx: range(omics$Pro_TE, na.rm = T)
      labs( title = 'All term genes in NW',
            subtitle = paste0('KD: ', kd, '\nTerm: ', term) )+
      theme_graph(background = 'white')
    ,
    ggraph(g2, layout = 'linear', circular = TRUE) +
            geom_edge_arc(alpha = .3, color = 'grey75') +
      geom_node_point( shape = 21, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter= .N()$name != kd)  )+
      geom_node_point( shape = 23, color = "black", alpha = .3,
        aes(size = TargetRiskScore, fill = Pro_EffectScore, filter = .N()$name == kd) )+
      geom_node_text(aes(label = name), size = 2) +
      coord_fixed() +
      scale_size_continuous( range = c(.5, 10), limits = c(0, 5), trans = 'exp')+
      scale_fill_gradient2(
        low = 'purple', mid = 'grey20', high = 'green', na.value = 'grey85',
        limits = c(-2.5,2.5) )+ #approx: range(omics$Pro_TE, na.rm = T)
      labs( title = 'Term genes & KD neighbors in NW',
            subtitle = paste0('KD: ', kd, '\nTerm: ', term) )+
      theme_graph(background = 'white')
    ,
    ncol = 2
    
  )
}
```

<!-- ## kda data -->
<!-- functions to read KDA results and plot sub-networks from identified key drivers -->
<!-- ```{r} -->
<!-- read_kda_res <- function(ef0_synID, ef1_synID, ef1_top){ -->

<!--   res = bind_rows( -->
<!--     read_tsv(synGet(ef0_synID)$path, col_types = cols()) %>% mutate(ef = 'ef0_fdr'), -->
<!--     read_tsv(synGet(ef1_synID)$path, col_types = cols()) %>% mutate(ef = 'ef1_fdr') -->
<!--   ) %>% -->
<!--   mutate(FDR = -log10(FDR)) %>% -->
<!--   pivot_wider(id_cols = c(MODULE, NODE, MEMBER), names_from = ef, values_from = FDR) %>% -->
<!--   mutate(across(contains('_fdr'), ~ if_else(is.na(.x), 0, .x))) %>%  -->
<!--   mutate(delta_fdr = ef1_fdr - ef0_fdr) %>% arrange(desc(delta_fdr)) %>%  -->
<!--   mutate(top = 0) -->

<!--   top = read_tsv(synGet(ef1_top)$path, col_types = cols()) %>%  -->
<!--     mutate(kd = paste0(NODE,'-',MODULE)) -->

<!--   if( any( top$FDR < 0.05 ) ){ -->
<!--     res$top[ which(paste0(res$NODE,'-',res$MODULE) %in% top$kd[top$FDR < 0.05]) ] <- 1 -->
<!--   } -->

<!--   return(res) -->

<!-- } -->


<!-- plot_kd_subnet <- function(nw, kd, term) { -->

<!--   vert_num <- match(kd, V(nw)$name) -->

<!--   vert_neigh <- neighbors(nw, vert_num) -->

<!--   term_num <- biodom %>% -->
<!--     filter(GOterm_Name == term) %>% -->
<!--     pull(symbol) %>% unlist() %>% -->
<!--     match(., V(nw)$name) %>% .[!is.na(.)] -->

<!--   g2 <- induced_subgraph(nw, c(vert_num, intersect(term_num, vert_neigh))) -->
<!--   g3 <- induced_subgraph(nw, c(vert_num, term_num)) -->

<!--   cowplot::plot_grid( -->

<!--     ggraph(g3, layout = 'linear', circular = TRUE) + -->
<!--       geom_edge_arc(alpha = .3, color = 'grey75') + -->
<!--       geom_node_point( shape = 21, color = "black", alpha = .3, -->
<!--         aes(size = TargetRiskScore, fill = Pro_EffectScore, filter= .N()$name != kd)  )+ -->
<!--       geom_node_point( shape = 23, color = "black", alpha = .3, -->
<!--         aes(size = TargetRiskScore, fill = Pro_EffectScore, filter = .N()$name == kd) )+ -->
<!--       geom_node_text(aes(label = name), size = 2) + -->
<!--       coord_fixed() + -->
<!--       scale_size_continuous( range = c(.5, 10), limits = c(0, 5), trans = 'exp')+ -->
<!--       scale_fill_gradient2( -->
<!--         low = 'purple', mid = 'grey20', high = 'green', na.value = 'grey85', -->
<!--         limits = c(-2.5,2.5) )+ #approx: range(omics$Pro_TE, na.rm = T) -->
<!--       labs( title = 'All term genes in NW', -->
<!--             subtitle = paste0('KD: ', kd, '\nTerm: ', term) )+ -->
<!--       theme_graph(background = 'white') -->
<!--     , -->
<!--     ggraph(g2, layout = 'linear', circular = TRUE) + -->
<!--             geom_edge_arc(alpha = .3, color = 'grey75') + -->
<!--       geom_node_point( shape = 21, color = "black", alpha = .3, -->
<!--         aes(size = TargetRiskScore, fill = Pro_EffectScore, filter= .N()$name != kd)  )+ -->
<!--       geom_node_point( shape = 23, color = "black", alpha = .3, -->
<!--         aes(size = TargetRiskScore, fill = Pro_EffectScore, filter = .N()$name == kd) )+ -->
<!--       geom_node_text(aes(label = name), size = 2) + -->
<!--       coord_fixed() + -->
<!--       scale_size_continuous( range = c(.5, 10), limits = c(0, 5), trans = 'exp')+ -->
<!--       scale_fill_gradient2( -->
<!--         low = 'purple', mid = 'grey20', high = 'green', na.value = 'grey85', -->
<!--         limits = c(-2.5,2.5) )+ #approx: range(omics$Pro_TE, na.rm = T) -->
<!--       labs( title = 'Term genes & KD neighbors in NW', -->
<!--             subtitle = paste0('KD: ', kd, '\nTerm: ', term) )+ -->
<!--       theme_graph(background = 'white') -->
<!--     , -->
<!--     ncol = 2 -->

<!--   ) -->
<!-- } -->
<!-- ``` -->

# Biodom NW analysis

Explore the effects of NW filters on traces & KDs for these sets:
• node & edge filtering effects
• direct edge filter before vs after trace
• nodes added by trace
• common vs unique nodes across BD
<!-- • KDA on full (i.e. not BD filtered) NW objects -->

## Cross NW comparisions

```{r}
nw.dat = doms %>% 
  # filter(bd.filt) %>% 
  select(bd:i) 

future::plan('multisession')
x = furrr::future_map_dfr(
  nw.dat$i,
  ~{synLogin()
    nw = read_nw(.x)
    snw = igraph::simplify(nw, remove.multiple = T)
    tibble(
      avg_node_degree = degree(snw, V(snw)) %>% mean(),
      avg_path_length = snw %>% average.path.length,
      assortativity_coef = snw %>% assortativity(., types1 = V(.)),
      connected_components = snw %>% no.clusters,
      edges = E(nw)$edge %>% unique() %>% list(),
      s.edges = E(snw)$edge %>% unique() %>% list(),
      nodes = V(nw) %>% names() %>% unique() %>% list(),
      s.nodes = V(snw) %>% names() %>% unique() %>% list()
    )
  }
)
future::plan('sequential')

nw.dat = bind_cols(nw.dat, x)

nw.dat$q_genes <- map(
  1:nrow(nw.dat),
  ~ doms$nw.dir[[.x]] %>% filter( grepl('queryList', name) ) %>% 
    pull(id) %>% synGet(.) %>% .$path %>% 
    read_tsv(., col_names = F, col_types = cols()) %>% 
    pull(X1) 
)

nw.dat$input_genes <- map(
  1:nrow(nw.dat),
  ~ intersect( unlist(nw.dat$q_genes[.x]), names(V(undir_node_edge)) )
)

nw.dat$added_genes <- map(
  1:nrow(nw.dat),
  ~ setdiff( nw.dat$nodes[[.x]], nw.dat$input_genes[[.x]] ) 
)

# -common nodes
# V(nw) %>% names() %>% unique() %>% length()
# -common edges
# E(nw)$edge %>% head()
#  by filt, direction
```

### NW size
```{r}
nw.summary <- nw.dat %>% 
  group_by(bd) %>% 
  summarise(
    q_genes = length(unique(unlist(q_genes))),
    n_nodes = length(unique(unlist(nodes))),
    n_edges = length(unique(unlist(edges)))
  ) %>% 
  mutate(
    n_possible_edge = (n_nodes * (n_nodes-1))/2,
    fxn_possible = n_edges/n_possible_edge
  )

# to calculate the number of possible edges in a graph with N nodes
# directed graph: N*(N-1)
# undriected graph: (N * (N-1)) / 2
nw.summary$n_possible_edge = map_dbl(1:nrow(nw.summary), ~ ( nw.summary$n_nodes[.x] * (nw.summary$n_nodes[.x]-1)) / 2)
nw.summary$fxn_possible = map_dbl(1:nrow(nw.summary), ~ nw.summary$n_edges[.x] / nw.summary$n_possible_edge[.x] )
```

```{r fig.width=7, fig.height=3}
nw.summary %>% 
  mutate(bd = str_replace_all(bd, '_' ,' ')) %>% 
  left_join(., biodom %>% select(bd = Biodomain, color, abbr ) %>% distinct() ) %>% 
  # filter(dir == 'undirected', filt == 'node_edge') %>% 
  pivot_longer(cols = c(n_nodes, n_edges, fxn_possible)) %>% 
  mutate( 
    max = case_when(
      name == 'n_nodes' ~ V(undir_node_edge) %>% length(),
      name == 'n_edges' ~ E(undir_node_edge) %>% length(),
      name == 'fxn_possible' ~ integer(1)),
    name = fct_relevel(name, c('n_nodes','n_edges', 'fxn_possible'))
    ) %>% 
  ggplot(aes(q_genes, value))+
  geom_point(aes(fill = color), size = 3, alpha = .5, shape = 21)+
  ggrepel::geom_text_repel(aes(label = abbr), size = 2.5)+
  geom_hline(aes(yintercept = max), lty = 2)+
  scale_y_log10()+
  scale_fill_identity()+
  labs(x = '# query genes', y = '# NW features')+
  # geom_smooth()+
  facet_wrap(~name, scales = 'free')
```



### NW properties
Global properties of biodomain-filtered path traced networks
```{r fig.width=18, fig.height=4}
nw.dat %>% 
  mutate(bd = str_replace_all(bd, '_' ,' ')) %>% 
  left_join(., biodom %>% select(bd = Biodomain, color, abbr ) %>% distinct() ) %>% 
  # filter(bd == dom) %>%
  select(-s.edges, -q_genes, -s.nodes) %>% 
  rowwise() %>%
  mutate( across( edges:added_genes, ~ length(unique(unlist(.x))) ),
          fxn_added = added_genes/nodes,
          total_possible_edge = (nodes*(nodes-1))/2,
          fxn_possible_edge = edges/total_possible_edge) %>% 
  pivot_longer(cols = c(avg_node_degree:added_genes, fxn_added, fxn_possible_edge), names_to = 'properties', values_to = 'val') %>% 
  mutate(properties = factor(properties,
                             levels = c('input_genes',
                                        'nodes',
                                        'added_genes',
                                        'fxn_added',
                                        
                                        'edges',
                                        'fxn_possible_edge',
                                        'connected_components',
                                        
                                        'avg_node_degree',
                                        'assortativity_coef',
                                        'avg_path_length'
                                        
                                        )),
         bd = factor(bd, 
                     levels = nw.dat %>% select(bd,input_genes) %>% 
                       mutate(input_genes = length(unique(unlist(input_genes)))) %>% 
                       arrange(input_genes) %>% pull(bd) %>% str_replace_all(., '_' ,' ')
                     )
         ) %>% 
  ggplot(aes(val, bd)) +
  geom_bar(stat = 'identity', position = 'dodge', aes(fill = color), 
           alpha = .8, color = 'grey30', width = .7)+
  theme(legend.position = 'top')+
  labs(y = '',x = '')+
  scale_fill_identity()+
  # scale_y_log10()+
  facet_wrap(~properties, scales = 'free_x', nrow = 1)

```

### Input Overlap
Query genes
```{r fig.width=8, fig.height=7}

olap <- crossing(nw1 = nw.dat$bd, nw2 = nw.dat$bd) %>% 
  group_by(nw1,nw2) %>% 
  mutate(.keep = 'all', 
         intersect = length(intersect(
           nw.dat %>% filter(bd == nw1) %>% pull(q_genes) %>% unlist(),
           nw.dat %>% filter(bd == nw2) %>% pull(q_genes) %>% unlist()
           ))
         ) %>% 
  ungroup() %>% group_by(nw1) %>% 
  mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
  ungroup() %>%
  mutate(
    nw1 = fct_relevel(
      nw1, 
      nw.dat %>% select(bd, q_genes) %>% distinct() %>% 
        mutate(len = length(unlist(q_genes))) %>% arrange(len) %>% pull(bd)
                      ),
    nw2 = fct_relevel(
      nw2, 
      nw.dat %>% select(bd, q_genes) %>% distinct() %>% 
        mutate(len = length(unlist(q_genes))) %>% arrange(desc(len)) %>% pull(bd)
                      )
  ) 

ggplot(olap, aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap), alpha = .8) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  viridis::scale_fill_viridis("% Total", option = "C", direction = -1)+
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'Query Genes') 

```

input genes (overlap with base net)
```{r fig.width=8, fig.height=7}

olap <- crossing(nw1 = nw.dat$bd, nw2 = nw.dat$bd) %>% 
    group_by(nw1,nw2) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             nw.dat %>% filter(bd == nw1) %>% pull(input_genes) %>% unlist(),
             nw.dat %>% filter(bd == nw2) %>% pull(input_genes) %>% unlist()
             )),
             len_nw1 = nw.dat %>% filter(bd == nw1) %>% pull(input_genes) %>% unlist() %>% length(),
             len_nw2 = nw.dat %>% filter(bd == nw2) %>% pull(input_genes) %>% unlist() %>% length()
           ) %>% 
    ungroup() %>% group_by(nw1) %>% 
    mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
    ungroup()

olap <- olap %>% 
    mutate(
      nw1 = fct_relevel(nw1, olap %>% select(nw1, len_nw1) %>% distinct() %>% arrange(len_nw1) %>% pull(nw1)),
      nw2 = fct_relevel(nw2, olap %>% select(nw1, len_nw1) %>% distinct() %>% arrange(desc(len_nw1)) %>% pull(nw1))
    ) 

olap %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap), alpha = .8) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  viridis::scale_fill_viridis("% Total", option = "C", direction = -1)+
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'input genes', subtitle = 'query overlap with filtered base network nodes') 

```



### Common Nodes
undirected
```{r fig.width=8, fig.height=7}
olap <- crossing(nw1 = nw.dat$bd, nw2 = nw.dat$bd) %>% 
    group_by(nw1,nw2) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             nw.dat %>% filter(bd == nw1) %>% pull(nodes) %>% unlist(),
             nw.dat %>% filter(bd == nw2) %>% pull(nodes) %>% unlist()
             )),
             len_nw1 = nw.dat %>% filter(bd == nw1) %>% pull(nodes) %>% unlist() %>% length(),
             len_nw2 = nw.dat %>% filter(bd == nw2) %>% pull(nodes) %>% unlist() %>% length()
           ) %>% 
    ungroup() %>% group_by(nw1) %>% 
    mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
    ungroup()

olap <- olap %>% 
    mutate(
      nw1 = fct_relevel(nw1, olap %>% select(nw1, len_nw1) %>% distinct() %>% arrange(len_nw1) %>% pull(nw1)),
      nw2 = fct_relevel(nw2, olap %>% select(nw1, len_nw1) %>% distinct() %>% arrange(desc(len_nw1)) %>% pull(nw1))
    ) 

olap %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap), alpha = .8) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  viridis::scale_fill_viridis("% Total", option = "C", direction = -1)+
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'common nodes') 

```

### Common Edges
common edges
```{r fig.width=8, fig.height=7}

olap <- crossing(nw1 = nw.dat$bd, nw2 = nw.dat$bd) %>% 
    group_by(nw1,nw2) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             nw.dat %>% filter(bd == nw1) %>% pull(edges) %>% unlist(),
             nw.dat %>% filter(bd == nw2) %>% pull(edges) %>% unlist()
             )),
             len_nw1 = nw.dat %>% filter(bd == nw1) %>% pull(edges) %>% unlist() %>% length(),
             len_nw2 = nw.dat %>% filter(bd == nw2) %>% pull(edges) %>% unlist() %>% length()
           ) %>% 
    ungroup() %>% group_by(nw1) %>% 
    mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
    ungroup()

olap <- olap %>% 
    mutate(
      nw1 = fct_relevel(nw1, olap %>% select(nw1, len_nw1) %>% distinct() %>% arrange(len_nw1) %>% pull(nw1)),
      nw2 = fct_relevel(nw2, olap %>% select(nw1, len_nw1) %>% distinct() %>% arrange(desc(len_nw1)) %>% pull(nw1))
    ) 

olap %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap), alpha = .8) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  viridis::scale_fill_viridis("% Total", option = "C", direction = -1)+
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2) +
  labs(x='',y='', title = 'common edges') 

```


### Added Nodes
```{r }
olap <- crossing(nw1 = nw.dat$bd, nw2 = nw.dat$bd) %>% 
    group_by(nw1,nw2) %>% 
    mutate(.keep = 'all', 
           intersect = length(intersect(
             setdiff(
               nw.dat %>% filter(bd == nw1) %>% pull(nodes) %>% unlist(),
               nw.dat %>% filter(bd == nw1) %>% pull(q_genes) %>% unlist()),
             setdiff(               
               nw.dat %>% filter(bd == nw2) %>% pull(nodes) %>% unlist(),
               nw.dat %>% filter(bd == nw2) %>% pull(q_genes) %>% unlist())
             )),
             len_nw1 = setdiff(
               nw.dat %>% filter(bd == nw1) %>% pull(nodes) %>% unlist(),
               nw.dat %>% filter(bd == nw1) %>% pull(q_genes) %>% unlist()) %>% length(),
             len_nw2 = setdiff(
               nw.dat %>% filter(bd == nw2) %>% pull(nodes) %>% unlist(),
               nw.dat %>% filter(bd == nw2) %>% pull(q_genes) %>% unlist()) %>% length()
           ) %>% 
    ungroup() %>% group_by(nw1) %>% 
    mutate(.keep = 'all', pct_overlap = intersect / intersect[which(nw2 == nw1)]) %>% 
    ungroup()

olap <- olap %>% 
    mutate(
      nw1 = fct_relevel(nw1, olap %>% select(nw1, len_nw1) %>% distinct() %>% arrange(len_nw1) %>% pull(nw1)),
      nw2 = fct_relevel(nw2, olap %>% select(nw1, len_nw1) %>% distinct() %>% arrange(desc(len_nw1)) %>% pull(nw1))
    ) 

olap %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct_overlap), alpha = .8) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  viridis::scale_fill_viridis("% Total", option = "C", direction = -1)+
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = intersect ), size = 2.5) +
  labs(x='',y='', title = 'added nodes') 

```

### input, added, total nodes in common


```{r}
olap <- crossing(nw1 = nw.dat$bd, nw2 = nw.dat$bd) %>% 
  group_by(nw1,nw2) %>% 
  mutate(.keep = 'all', 
         
         input = length(intersect(
           nw.dat %>% filter(bd == nw1) %>% pull(input_genes) %>% unlist(),
           nw.dat %>% filter(bd == nw2) %>% pull(input_genes) %>% unlist()
           )),
         
         added = length(intersect(
           nw.dat %>% filter(bd == nw1) %>% pull(added_genes) %>% unlist(),
           nw.dat %>% filter(bd == nw2) %>% pull(added_genes) %>% unlist()
             )),
         
         total = length(intersect(
             nw.dat %>% filter(bd == nw1) %>% pull(nodes) %>% unlist(),
             nw.dat %>% filter(bd == nw2) %>% pull(nodes) %>% unlist()
             )),
         
         len_nw1 = nw.dat %>% filter(bd == nw1) %>% pull(nodes) %>% unlist() %>% length(),
         len_nw2 = nw.dat %>% filter(bd == nw2) %>% pull(nodes) %>% unlist() %>% length()
         
         ) %>% 
  ungroup() %>% group_by(nw1) %>% 
  mutate(.keep = 'all', 
         input_overlap = input / input[which(nw2 == nw1)],
         added_overlap = added / added[which(nw2 == nw1)],
         total_overlap = total / total[which(nw2 == nw1)],
         ) %>% 
  ungroup() 

olap <- olap %>% 
  pivot_longer(input:total, names_to = 'set', values_to = 'n') %>% 
  # pivot_longer(ends_with('_overlap')) %>% distinct() %>% 
  mutate(
    set = fct_relevel(set, c('total','input','added')), 
    pct = n / len_nw1,
    nw1 = fct_relevel(nw1, olap %>% select(nw1, len_nw1) %>% distinct() %>% arrange(len_nw1) %>% pull(nw1)),
    nw2 = fct_relevel(nw2, olap %>% select(nw1, len_nw1) %>% distinct() %>% arrange(desc(len_nw1)) %>% pull(nw1))
    ) 
```


```{r fig.width=18, fig.height=7}

olap %>% 
  ggplot(., aes(x = nw2, y = nw1)) +
  geom_tile(aes(fill=pct), alpha = .8) + theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  # theme(axis.text.x = element_blank(), legend.position = 'bottom') +
  # scale_fill_gradient2('% Total', low = 'white', high = '4a66ac', na.value = 'grey90') +
  viridis::scale_fill_viridis("% Total Nodes", option = "C", direction = -1)+
  # scale_x_discrete(position = "top") +
  geom_text(aes(label = round(pct,2) ), size = 2.5) +
  facet_wrap(~set, nrow = 1)+
  labs(x='',y='') 

```


### Score Comparisons (Query genes vs Added genes)
```{r}
tmp <- nw.dat %>% 
  select(bd, input_genes, added_genes) %>% 
  pivot_longer(cols = c(input_genes, added_genes)) %>% 
  unnest(value) %>% 
  left_join(
    .,
    scores %>% select(value = GeneName, Overall, 
                      GeneticsScore, OmicsScore, LiteratureScore),
    by = 'value', na_matches = 'never'
  ) %>% 
  bind_rows(
    scores %>% select(value = GeneName, Overall, 
                      GeneticsScore, OmicsScore, LiteratureScore) %>% 
      mutate(name = 'all_scores')
  ) %>% 
  mutate(
    name = factor(name, levels = c('input_genes','added_genes','all_scores'))
  )
```


```{r fig.width=5, fig.height=3}
tmp %>% 
  select(-bd) %>% distinct() %>% 
  rename(set = name, gene = value) %>% 
  ggplot(aes(Overall))+
  theme(legend.position = 'top') + 
  # geom_density(aes(fill = set, color = set), alpha = .3)
  geom_histogram(aes(fill = set), alpha = .8, position='dodge')
```

```{r fig.width=8, fig.height=3}
tmp %>% 
  select(-bd) %>% distinct() %>% 
  rename(set = name, gene = value) %>% 
  pivot_longer(Overall:OmicsScore) %>% 
  filter(value >0) %>% 
  ggplot(aes(value))+
  theme(legend.position = 'top') + 
  geom_density(aes(fill = set), color = 'grey70', alpha = .3)+
  # geom_histogram(aes(fill = set),  alpha = .8, position='dodge')+
  labs(x='score')+
  facet_grid(~name, scales = 'free')
```

```{r fig.width=6, fig.height=12}
tmp %>% 
  rename(set = name, gene = value) %>% 
  filter(set!='all_scores') %>% 
  pivot_longer(Overall:OmicsScore) %>% 
  filter(value > 0) %>% 
  ggplot(aes(value))+
  theme(legend.position = 'top') + 
  # geom_density(aes(fill = set, color = set), alpha = .3)+
  geom_histogram(aes(fill = set), alpha = .8, position='dodge')+
  facet_grid(bd~name, scales = 'free')
```

```{r fig.width=15, fig.height=6}
tmp %>% 
  filter( name != 'all_scores' ) %>% 
  rename(set = name, gene = value) %>% 
  ggplot(aes(Overall))+
  theme(legend.position = 'top') + 
  # geom_density(aes(fill = set), color = 'grey70', alpha = .3)+
  geom_histogram(aes(fill = set), alpha = .8, position='dodge')+
  labs(x = 'TREAT-AD Target Risk Score')+
  facet_wrap(~bd, scales = 'free', ncol = 6)
```

### Biodom Enrichment - NW nodes

```{r}
univ <-as.data.frame(org.Hs.eg.db::org.Hs.egGO) %>%
  pull(gene_id) %>%
  unique() %>%
  gprofiler2::gconvert(., organism = 'hsapiens', target = 'HGNC', numeric_ns = 'ENTREZGENE_ACC') %>% 
  as_tibble() %>% 
  pull('name') %>%
  intersect(., names(V(base_net)) )

gl <- nw.dat %>%
  select(bd, nodes, q_genes, added_genes) %>%
  pivot_longer(nodes:added_genes) %>%
  rowwise() %>%
  mutate(
    enr = gprofiler2::gost( query = unlist(value),
                            organism = 'hsapiens',
                            domain_scope = 'custom',
                            custom_bg = univ,
                            sources = 'GO'
                            ) %>%
      .$result %>%
      list(),
    enr = anno.enr(enr,
                   GO_ID_column = 'term_id',
                   biodomain_table = biodom,
                   domain_colors = biodom %>% select(domain = Biodomain, abbr:color) %>% distinct()) %>%
      list()
  ) %>% select(bd, name, value, enr) %>%
  unnest(enr)
```

```{r warning=FALSE, fig.width=10, fig.height=10}
thresh = 1e-25
  
tmp <- gl %>% filter(name == 'q_genes', Biodomain != 'none')

bdt <- bd.tally(tmp %>% filter(p_value <= thresh) %>% pull(term_name), biodom)

tmp = tmp %>%
  rowwise() %>%
  mutate(bd = paste0(bd,'\n', length(unique(unlist(value))), ' input genes') ) %>%
  mutate(Biodomain = factor(Biodomain,
                            levels = bdt$domain %>%
                              str_subset('none', negate = T) %>%
                              c('none',.))
         )

tmp %>%
  ggplot(aes(-log10(p_value), Biodomain))+
  geom_violin(data = subset(tmp, p_value <= thresh), aes(color = color), scale = 'width')+
  geom_jitter(data = subset(tmp, p_value <= thresh), aes(color = color), alpha = .7)+
  scale_color_identity()+
  # xlim(c(0,30))+
  labs(y = '', title = 'Input Genes', subtitle = paste0('enrichment threshold: ', thresh))+
  facet_wrap(~bd, ncol = 6) # , scales = 'free_x'
```

```{r warning=FALSE, fig.width=10, fig.height=10}
thresh = 1e-25

tmp <- gl %>% filter(name == 'nodes', Biodomain != 'none')

bdt <- bd.tally(tmp %>% filter(p_value <= thresh) %>% pull(term_name), biodom)

tmp = tmp %>%
  rowwise() %>%
  mutate(bd = paste0(bd,'\n', length(unique(unlist(value))), ' total nodes') ) %>%
  mutate(Biodomain = factor(Biodomain,
                            levels = bdt$domain %>%
                              str_subset('none', negate = T) %>%
                              c('none',.))
         )

tmp %>%
  ggplot(aes(-log10(p_value), Biodomain))+
  geom_violin(data = subset(tmp, p_value <= thresh), aes(color = color), scale = 'width')+
  geom_jitter(data = subset(tmp, p_value <= thresh), aes(color = color), alpha = .7)+
  scale_color_identity()+
  # xlim(c(0,30))+
  labs(y = '', title = 'Network Nodes', subtitle = paste0('enrichment threshold: ', thresh))+
  facet_wrap(~bd, ncol = 6) #, scales = 'free_x'
```

```{r warning=FALSE, fig.width=10, fig.height=10}
thresh = 1e-25

tmp <- gl %>% filter(name == 'added_genes', Biodomain != 'none')

bdt <- bd.tally(tmp %>% filter(p_value <= thresh) %>% pull(term_name), biodom)

tmp = tmp %>%
  rowwise() %>%
  mutate(bd = paste0(bd,'\n', length(unique(unlist(value))), ' nodes added') ) %>%
  mutate(Biodomain = factor(Biodomain,
                            levels = bdt$domain %>%
                              str_subset('none', negate = T) %>%
                              c('none',.))
         )

tmp %>%
  ggplot(aes(-log10(p_value), Biodomain))+
  geom_violin(data = subset(tmp, p_value <= thresh), aes(color = color), scale = 'width')+
  geom_jitter(data = subset(tmp, p_value <= thresh), aes(color = color), alpha = .7)+
  scale_color_identity()+
  # xlim(c(0,30))+
  labs(y = '', title = 'Nodes Added by Pathway Tracing', subtitle = paste0('enrichment threshold: ', thresh))+
  facet_wrap(~bd, ncol = 6) #, scales = 'free_x'
```

```{r warning=FALSE, fig.width=10, fig.height=10}
thresh = 1e-25

tmp <- gl %>% filter(Biodomain != 'none')

bdt <- bd.tally(tmp %>% filter(p_value <= thresh) %>% pull(term_name), biodom)

tmp = tmp %>%
  rowwise() %>%
  # mutate(bd = paste0(bd,'\n', length(unique(unlist(value))), ' nodes added') ) %>%
  mutate(
    Biodomain = factor( Biodomain, levels = bdt$domain %>% str_subset('none', negate = T) %>% c('none',.)),
    name = factor( name, levels = c('q_genes','added_genes','nodes') )
         )

```

```{r fig.width=20, fig.height=8}
tmp %>%
  ggplot(aes( -log10(p_value) , Biodomain ))+
  geom_violin(data = subset(tmp, p_value <= thresh), aes(color = color), scale = 'width')+
  geom_jitter(data = subset(tmp, p_value <= thresh), aes(color = color), alpha = .7)+
  scale_color_identity()+
  # xlim(c(0,30))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  labs(y = '', subtitle = paste0('enrichment threshold: ', thresh))+
  facet_grid(name~bd, scales = 'free_x') #, scales = 'free_x'

```

```{r warning=FALSE, fig.width=7, fig.height=4}
thresh = 1e-3

tmp <- gl %>% filter(bd == 'Mitochondrial_Metabolism', Biodomain != 'none')

bdt <- bd.tally(tmp %>% filter(p_value <= thresh) %>% pull(term_name), biodom)

tmp = tmp %>%
  rowwise() %>%
  # mutate(bd = paste0(bd,'\n', length(unique(unlist(value))), ' nodes added') ) %>%
  mutate(Biodomain = factor(Biodomain, levels = bdt$domain %>% str_subset('none', negate = T) %>%c('none',.)),
         name = factor(name, levels = c('q_genes', 'added_genes', 'nodes'))
         )

tmp %>%
  ggplot(aes(-log10(p_value), Biodomain))+
  geom_violin(data = subset(tmp, p_value <= thresh), aes(color = color), scale = 'width')+
  geom_jitter(data = subset(tmp, p_value <= thresh), aes(color = color), alpha = .7)+
  scale_color_identity()+
  # xlim(c(0,30))+
  labs(y = '', title = unique(tmp$bd), subtitle = paste0('enrichment threshold: ', thresh))+
  facet_wrap(~name, ncol = 6) #, scales = 'free_x'
```


```{r warning=FALSE, fig.width=7, fig.height=4}
thresh = 1e-3

tmp <- gl %>% filter(bd == 'Structural_Stabilization', Biodomain != 'none')

bdt <- bd.tally(tmp %>% filter(p_value <= thresh) %>% pull(term_name), biodom)

tmp = tmp %>%
  rowwise() %>%
  # mutate(bd = paste0(bd,'\n', length(unique(unlist(value))), ' nodes added') ) %>%
  mutate(Biodomain = factor(Biodomain, levels = bdt$domain %>% str_subset('none', negate = T) %>%c('none',.)),
         name = factor(name, levels = c('q_genes', 'added_genes', 'nodes'))
         )

tmp %>%
  ggplot(aes(-log10(p_value), Biodomain))+
  geom_violin(data = subset(tmp, p_value <= thresh), aes(color = color), scale = 'width')+
  geom_jitter(data = subset(tmp, p_value <= thresh), aes(color = color), alpha = .7)+
  scale_color_identity()+
  # xlim(c(0,30))+
  labs(y = '', title = unique(tmp$bd), subtitle = paste0('enrichment threshold: ', thresh))+
  facet_wrap(~name, ncol = 6) #, scales = 'free_x'
```

```{r warning=FALSE, fig.width=7, fig.height=4}
thresh = 1e-3

tmp <- gl %>% filter(bd == 'Immune_Response', Biodomain != 'none')

bdt <- bd.tally(tmp %>% filter(p_value <= thresh) %>% pull(term_name), biodom)

tmp = tmp %>%
  rowwise() %>%
  mutate(n2 = paste0(name,'\n', length(unique(unlist(value))) ) ) %>%
  mutate(Biodomain = factor(Biodomain, levels = bdt$domain %>% str_subset('none', negate = T) %>%c('none',.)),
         name = factor(name, levels = c('q_genes', 'added_genes', 'nodes'))
         )

tmp %>%
  ggplot(aes(-log10(p_value), Biodomain))+
  geom_violin(data = subset(tmp, p_value <= thresh), aes(color = color), scale = 'width')+
  geom_jitter(data = subset(tmp, p_value <= thresh), aes(color = color), alpha = .7)+
  scale_color_identity()+
  # xlim(c(0,30))+
  labs(y = '', title = unique(tmp$bd), subtitle = paste0('enrichment threshold: ', thresh))+
  facet_wrap(~name, ncol = 6) #, scales = 'free_x'
```

```{r warning=FALSE, fig.width=7, fig.height=4}
thresh = 1e-3

tmp <- gl %>% filter(bd == 'Synapse', Biodomain != 'none')

bdt <- bd.tally(tmp %>% filter(p_value <= thresh) %>% pull(term_name), biodom)

tmp = tmp %>%
  rowwise() %>%
  mutate(n2 = paste0(name,'\n', length(unique(unlist(value))) ) ) %>%
  mutate(Biodomain = factor(Biodomain, levels = bdt$domain %>% str_subset('none', negate = T) %>%c('none',.)),
         name = factor(name, levels = c('q_genes', 'added_genes', 'nodes'))
         )

tmp %>%
  ggplot(aes(-log10(p_value), Biodomain))+
  geom_violin(data = subset(tmp, p_value <= thresh), aes(color = color), scale = 'width')+
  geom_jitter(data = subset(tmp, p_value <= thresh), aes(color = color), alpha = .7)+
  scale_color_identity()+
  # xlim(c(0,30))+
  labs(y = '', title = unique(tmp$bd), subtitle = paste0('enrichment threshold: ', thresh))+
  facet_wrap(~name, ncol = 6) #, scales = 'free_x'
```

```{r warning=FALSE, fig.width=7, fig.height=4}
thresh = 1e-3

tmp <- gl %>% filter(bd == 'APP_Metabolism', Biodomain != 'none')

bdt <- bd.tally(tmp %>% filter(p_value <= thresh) %>% pull(term_name), biodom)

tmp = tmp %>%
  rowwise() %>%
  mutate(n2 = paste0(name,'\n', length(unique(unlist(value))) ) ) %>%
  mutate(Biodomain = factor(Biodomain, levels = bdt$domain %>% str_subset('none', negate = T) %>%c('none',.)),
         name = factor(name, levels = c('q_genes', 'added_genes', 'nodes'))
         )

tmp %>%
  ggplot(aes(-log10(p_value), Biodomain))+
  geom_violin(data = subset(tmp, p_value <= thresh), aes(color = color), scale = 'width')+
  geom_jitter(data = subset(tmp, p_value <= thresh), aes(color = color), alpha = .7)+
  scale_color_identity()+
  # xlim(c(0,30))+
  labs(y = '', title = unique(tmp$bd), subtitle = paste0('enrichment threshold: ', thresh))+
  facet_wrap(~name, ncol = 6) #, scales = 'free_x'
```

```{r warning=FALSE, fig.width=7, fig.height=4}
thresh = 1e-3

tmp <- gl %>% filter(bd == 'Tau_Homeostasis', Biodomain != 'none')

bdt <- bd.tally(tmp %>% filter(p_value <= thresh) %>% pull(term_name), biodom)

tmp = tmp %>%
  rowwise() %>%
  mutate(n2 = paste0(name,'\n', length(unique(unlist(value))) ) ) %>%
  mutate(Biodomain = factor(Biodomain, levels = bdt$domain %>% str_subset('none', negate = T) %>%c('none',.)),
         name = factor(name, levels = c('q_genes', 'added_genes', 'nodes'))
         )

tmp %>%
  ggplot(aes(-log10(p_value), Biodomain))+
  geom_violin(data = subset(tmp, p_value <= thresh), aes(color = color), scale = 'width')+
  geom_jitter(data = subset(tmp, p_value <= thresh), aes(color = color), alpha = .7)+
  scale_color_identity()+
  # xlim(c(0,30))+
  labs(y = '', title = unique(tmp$bd), subtitle = paste0('enrichment threshold: ', thresh))+
  facet_wrap(~name, ncol = 6) #, scales = 'free_x'
```

# Session
```{r}
sessionInfo()
```

